---
title: "Descriptive statistics"
author: "Anuschka Peelen"
date: "`r Sys.Date()`"
output: html_document
---

```{r, echo=FALSE}
#knitr::opts_chunk$set(eval = FALSE)
knitr::opts_chunk$set(number_sections = FALSE)
options(width = 100)
colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }
```


```{css, echo=FALSE}
pre {
  max-height: 300px;
  overflow-y: auto;
}

pre[class] {
  max-height: 100px;
}
```

In this script, I write the code to make some plots and tables that I use in the data and analysis section. You will find the code for the plot with datasets per year, the Table with individual regression analysis for one variable of ISSP and the Table with all the pooled effects. 

```{r,results='hide', warning=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(kableExtra)
library(modelsummary)
library(tidyverse)
library(writexl)
library(readxl)
library(gamlss)
library(metafor)
library(meta)
library(ggrepel)
rm(list=ls())
```

## Ggplot that shows the years that each dataset covers {-}

```{r}
datayear <- read_excel("./data/descriptives/dataset_year.xlsx")
datayear <- as.data.frame(datayear)
```

```{r, warning=FALSE, fig.show='asis'}
color_scale <- c ("#E02023", "#1676E3", "#20C66B", "#1ABC9C", "#85C1E9" , "#EB984E", "#AF7AC5" , "#F1C40F")
datayear$dataset <- factor(datayear$dataset, levels = c("MOT", "SOCON", "LISS", "I&O", "ESS", "ISSP", "EVS", "EB"))
datayear$color[datayear$dataset == "I&O"] <- "#1ABC9C"
datayear$color[datayear$dataset == "ESS"] <- "#85C1E9"
datayear$color[datayear$dataset == "ISSP"] <- "#EB984E"
datayear$color[datayear$dataset == "EVS"] <- "#AF7AC5"
datayear$color[datayear$dataset == "EB"] <- "#F1C40F"
datayear$color[datayear$dataset == "MOT"] <- "#E02023"
datayear$color[datayear$dataset == "SOCON"] <- "#1676E3"
datayear$color[datayear$dataset == "LISS"] <- "#20C66B"

first_last_year <- datayear %>%
  group_by(dataset) %>%
  summarize(first_year = min(year),
            last_year = max(year))

yearplot <- ggplot(data = datayear, aes(x = year, y = dataset, color = color)) +
  geom_point(size = 2) +
  geom_line(aes(group = dataset), size = 1) +
  geom_text(data = first_last_year, aes(x = first_year, y = dataset, label = as.character(first_year)),
            vjust = -1, color = "darkgrey", size = 3, show.legend = FALSE) + 
    geom_text(data = first_last_year, aes(x = last_year, y = dataset, label = as.character(last_year)),
            vjust = -1, color = "darkgrey", size = 3, show.legend = FALSE) +
  scale_color_manual(values = color_scale) +
  labs(x = "Year", y = "Dataset") +
  theme_classic() + 
  theme(legend.position = "none")
print(yearplot)

ggsave("yearplot.png", width = 7, height = 5, path = "./output/yearplot_APRIL25.png")


```


## Make the same table as above, but then per item to get an overview of when these were asked. 

```{r}
rm(list=ls())
load("./data/meta_analysis/total_reg_results_gam_w_new.RData")

total_reg_results <- subset(total_reg_results, subset = dep_var != "cc_unstop")

itemplot <- total_reg_results %>%
  select(dep_var, dep_var_name, nr_waves, first_year, data)

itemplot_x <- itemplot %>%
  uncount(nr_waves) %>%  
  group_by(dep_var) %>%  
  dplyr::mutate(wave = row_number()) %>%  
  ungroup() 

itemplot_x <- itemplot_x %>%
  mutate(surveyyear = case_when(
    data == "ESS" & wave == 1 ~ 2016,
    data == "ESS" & wave == 2 ~ 2020, 
    data == "EVS" & wave == 1 ~ 1990,
    data == "EVS" & wave == 2 ~ 1999,
    data == "EVS" & wave == 3 ~ 2008,
    data == "IO" & wave == 1 ~ 2019,
    data == "IO" & wave == 2 ~ 2020,
    data == "IO" & wave == 3 ~ 2022,
    data == "MOT" & wave == 1 ~ 2019,
    data == "MOT" & wave == 2 ~ 2021,
    data == "SOCON" & wave == 1 ~ 2019,
    data == "SOCON" & wave == 2 ~ 2020,
    data == "SOCON" & wave == 3 ~ 2022,
    data == "LISS" & wave == 1 ~ 2020,
    data == "LISS" & wave == 2 ~ 2020,
    data == "LISS" & wave == 3 ~ 2021,
  ))


#write.csv(itemplot_x, "./data/descriptives/itemplot.csv")
itemplot_df <- read_excel("./data/descriptives/itemplot.xlsx")

first_last_year <- itemplot_df %>%
  ungroup() %>%
  dplyr::group_by(dep_var_name) %>%
  dplyr::summarize(first_year = min(surveyyear),
            last_year = max(surveyyear))


colors <- total_reg_results %>%
  dplyr::group_by(dep_var) %>%
  dplyr::summarize(colour, 
            year_mean) 

itemplot_df <- itemplot_df %>%
  left_join(colors, by = "dep_var")

# There are a few different variables with the same variable name
itemplot_df$dep_var_name[itemplot_df$dep_var=="cc_prsact"] <- "Youve taken action"
itemplot_df$dep_var_name[itemplot_df$dep_var=="fut_gen_socon"] <- "Worry fut gen socon"
itemplot_df$dep_var_name[itemplot_df$dep_var=="resp_citiz_mot"] <- "Resp citizen mot"

itemplot <- ggplot(data = itemplot_df, aes(x = surveyyear, y = dep_var_name)) +
  geom_point(size = 1.2, aes(color = colour)) +  # Color legend
  geom_line(aes(group = dep_var_name, color = colour), size = 1) +  # Line legend (uses same color)
  geom_point(aes(x = year_mean, shape = "Mean Year"), color = "darkgrey", size = 2) +  # Diamond legend
  labs(x = "Year", y = "Item", color = "Category", shape = " ") + 
    scale_color_manual(
    values = c("#B0CC52" = "#B0CC52", "#CC5279" = "#CC5279", "#2980B9" = "#2980B9"),  # Assigns colors
    labels = c("#B0CC52" = "Behavioral", "#CC5279" = "Affective", "#2980B9" = "Cognitive")  # Custom names
  ) + 
  scale_shape_manual(values = c("Mean Year" = 19)) +  # Assigns the diamond shape
  theme_classic() + 
  theme(text = element_text(size = 5))

ggsave("itemplot.png", width = 7, height = 5, path = "./output/itemplot.png")

```




## Table of the GAMLSS regression output {-}

```{r}
# Run this piece of code so that in the Table beneath it will not show NAs
options(knitr.kable.NA = '')

```

```{r, eval=FALSE}
# Illustrate the gamlss regressions by showing one from ISSP with kable extra
load("./data/final_data/regression_outputs/issp_list_empty_w.Rdata")
load("./data/final_data/regression_outputs/issp_list_preds_w_new.Rdata")
load("./data/final_data/regression_outputs/issp_list_interactions_w_new.Rdata"))

# Use first variable, which is "worry"
model_time_only <- summary(issp_list_empty[[1]])
model_time_only_df <- as.data.frame(model_time_only)
model_time_only_df$mu_sigma <- c("Mu", "", "Sigma", "")
model_time_only_df$variables <- c("Intercept", "Time", "Intercept", "Time")
model_time_only_df <- model_time_only_df %>% dplyr:: select(mu_sigma, variables, everything())
rownames(model_time_only_df) <- NULL

model_indep_df <- as.data.frame(summary(issp_list_preds[[1]]))
model_indep_df$mu_sigma <- c("Mu", "", "", "", "", "","Sigma", "", "", "", "", "")
model_indep_df$variables <- c("Intercept", "Time", "Gender",  "Isced intermediate (ref=basic)", "Isced advanced (ref=basic)", "Age", "Intercept", "Time", "Gender",  "Isced intermediate (ref=basic)", "Isced advanced (ref=basic)", "Age")
model_indep_df <- model_indep_df %>% dplyr::select(mu_sigma, variables, everything())
rownames(model_indep_df) <- NULL

model_interact_df <- as.data.frame(summary(issp_list_interactions[[1]]))
model_interact_df$mu_sigma <- c("Mu", "", "", "", "", "", "", "", "", "", "Sigma", "", "", "", "", "", "", "", "", "")
model_interact_df$variables <- c("Intercept", "Time", "Gender",  "Isced intermediate (ref=basic)", "Isced advanced (ref=basic)", "Age", "Age x time", "Gender x time", "Isced intermediate x time", "Isced advanced x time", "Intercept", "Time", "Gender",  "Isced intermediate (ref=basic)", "Isced advanced (ref=basic)", "Age", "Age x time", "Gender x time", "Isced intermediate x time", "Isced advanced x time")
model_interact_df <- model_interact_df %>% dplyr::select(mu_sigma, variables, everything())
rownames(model_interact_df) <- NULL

# Difficult to columnbind them, because they're of different lengths (logically), so use a function
df_list <- list(model_time_only_df, model_indep_df, model_interact_df)

bind_cols_fill <- function(df_list) {

  max_rows <- map_int(df_list, nrow) %>% max()
  
  map(df_list, function(df) {
    if(nrow(df) == max_rows) return(df)
    first <- names(df)[1] %>% sym()
    df %>% add_row(!!first := rep(NA, max_rows - nrow(df)))
  }) %>% bind_cols()
}

model_total <- bind_cols_fill(df_list)

model_total[is.na(model_total)] <- ""

# The dataframe is binded, the order is not totally how i want it. The data are now all centered at the top, but for the 
# previous models, I need the data to be centered around the mu/intercept and sigma/intercept (with a lot of blank spaces). # Furthermore, some variables have a name that has special signs in them, which causes R not to recognize them. To make it #easy, I quickly fix these things in Excel. I don't make any changes to the data
#write_xlsx(model_total, "./data/descriptives/kable_model_total_gamlss.xlsx" )
```


```{r}
model_new <- read_excel("./data/descriptives/kable_model_total_gamlss.xlsx" )

# I Want to round the numeric variables to 3 decimals
model_new <- dplyr::mutate(model_new, across(.cols = c(-mu_sigma, -variables), .fns= as.numeric))
numeric_cols <- sapply(model_new, is.numeric)
model_new[, numeric_cols] <- round(model_new[, numeric_cols], digits = 3)

# There are some annoying variable names that R can't recognize because it has spacing, so rename the columns
colnames(model_new) <- (c("mu_sigma", "Variables", "est_time", "std_err_time", "p_time", "est_indep", "std_err_indep", "p_indep", "est_inter", "std_error_inter", "p_inter", "p_text_time_only", "p_text_indep", "p_text_inter"))

# Create a new variable to use stars instead of the full p-values in the table
model_new$p_text_time_only <- case_when(
  model_new$p_time >= 0.05 ~ "",
model_new$p_time < 0.001 ~ "***",
model_new$p_time < 0.01 ~ "**",
model_new$p_time < 0.05 ~ "*"
)

model_new$p_text_indep <- case_when(
  model_new$p_indep >= 0.05 ~ "",
model_new$p_indep < 0.001 ~ "***",
model_new$p_indep < 0.01 ~ "**",
model_new$p_indep < 0.05 ~ "*"
)

model_new$p_text_inter <- case_when(
  model_new$p_inter >= 0.05 ~ "",
model_new$p_inter < 0.001 ~ "***",
model_new$p_inter < 0.01 ~ "**",
model_new$p_inter < 0.05 ~ "*"
)

# Now only select the variables that I want to show in the table
model_new <- dplyr::select(model_new, mu_sigma, Variables, est_time, std_err_time, p_text_time_only, est_indep, std_err_indep, p_text_indep, est_inter, std_error_inter, p_text_inter)

# Make and save the table 
kable(model_new, digits = 3, caption = "Table 2. GAMLSS model on worry ISSP (1993 - 2010)", 
      col.names = c( "", "Variables", "Estimate", "Std. Error", "", "Estimate", "Std. Error", "", "Estimate", "Std. Error", ""), align = "l") %>%
  kable_classic_2(html_font = "Times", fixed_thead = T, full_width = F) %>%
  add_header_above(c(" " = 2, "Time-only model" = 3, "Indepent var model" = 3, "Interaction model" = 3), align = "l") %>%
   footnote(
    general_title = "Note.",
    general = "*** = p < 0.001, ** = p < 0.01, * = p < 0.05",
    threeparttable = TRUE,
    footnote_as_chunk = TRUE
    ) 
#%>%
    #save_kable("/Users/anuschka/Documents/climatechange/climatechange/output/gamlss_table.pdf")
  
```

## Table all pooled effects {-}

```{r, eval=false}
#First, I have to make sure all sigma effects have a common benchmark. I thus divide them by the intercept of t0
rm(list=ls())
load("./data/meta_analysis/total_reg_results_gam_w_new.RData")
total_reg_results$sig_time_std <- total_reg_results$sig_time/total_reg_results$sigma_intercept
total_reg_results$sig_time_sd_std <- total_reg_results$sig_time_sd/total_reg_results$sigma_intercept

total_reg_results$sig_time_pred_std <- total_reg_results$sig_time_pred/total_reg_results$sigma_intercept
total_reg_results$sig_time_sd_pred_std <- total_reg_results$sig_time_sd_pred/total_reg_results$sigma_intercept

total_reg_results$sig_time_int_std <- total_reg_results$sig_time_int/total_reg_results$sigma_intercept
total_reg_results$sig_time_sd_int_std <- total_reg_results$sig_time_sd_int/total_reg_results$sigma_intercept
#save(total_reg_results, file = "./data/meta_analysis/total_reg_results_gam_w_new.RData")

load("./data/meta_analysis/total_indep_var_results_new.RData")
total_indep_var_results <- total_indep_var_results %>%
  mutate(across(c(sig_sex_est:sig_age_sd), ~./total_reg_results$sigma_intercept, .names = "{.col}_std"))
save(total_indep_var_results, file= "./data/meta_analysis/total_indep_var_results_new.RData")

load("./data/meta_analysis/total_inter_results_new.RData")

total_inter_results <- total_inter_results %>%
  mutate(across(c(sig_sex_est:sig_age_sd), ~./total_reg_results$sigma_intercept, .names = "{.col}_std"))

total_inter_results <- total_inter_results %>%
  mutate(across(c(sig_sex_est_inter:sig_age_sd_inter), ~./total_reg_results$sigma_intercept, .names = "{.col}_std"))

save(total_inter_results, file = "./data/meta_analysis/total_inter_results_new.RData")

```


```{r, eval=FALSE }
#rm(list=ls())
# I want to repeat the above Table, but instead of regressions I now want to put all the pooled effects in there
# Starting with the time only model
# You may notice that I use the rma function and metagen. The estimate TE.random of metagen (pooled effect) is the same as the beta in the rma model
set.seed(1) #(as I am performing analyses with a random aspect)

#load("./data/meta_analysis/total_reg_results_gam_w_new.RData")

# Delete outlier
total_reg_results <- subset(total_reg_results, subset = dep_var != "cc_unstop")

# Extract the pooled effects, first mean attitudes
model_step_1_att <- rma(yi = mu_time,
              sei = mu_time_sd,
              data = total_reg_results,
              method = "ML",
              test = "knha")

one <- summary(model_step_1_att)
one_df <- data.frame(matrix(ncol = 5, nrow = 1))
colnames(one_df) <- c("mu_sigma", "Variable", "Estimate", "SE", "p")

one_df$mu_sigma <- c("Mean attitudes")
one_df$Variable <- "Time"
one_df$Estimate <- as.numeric(one$b)
one_df$SE <- one$se
one_df$p <- one$pval

# And now variance
model_step_1_var <- rma(yi = sig_time,
              sei = sig_time_sd,
              data = total_reg_results,
              method = "ML",
              test = "knha")

two <- summary(model_step_1_var)
two_df <- data.frame(matrix(ncol = 5, nrow = 1))
colnames(two_df) <- c("mu_sigma", "Variable", "Estimate", "SE", "p")

two_df$mu_sigma <- c("Polarization attitudes")
two_df$Variable <- "Time"
two_df$Estimate <- as.numeric(two$b)
two_df$SE <- two$se
two_df$p <- two$pval

# Rowbind them, these are all the pooled effects of the time-only model
empty_df <- rbind(one_df, two_df)

# Now continue with the independent variable model, first the mean attitudes 
load("./data/meta_analysis/total_indep_var_results_new.RData")

# Delete outlier
total_indep_var_results <- subset(total_indep_var_results, subset = dep_var != "cc_unstop")

m2_att <- rma(yi = mu_time_pred,
              sei = mu_time_sd_pred,
              data = total_reg_results,
              method = "ML",
              test = "knha")

# Gender 
gender_gen <- metagen(TE = mu_sex_est,
                 seTE = mu_sex_sd,
                 data = total_indep_var_results,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "ML",
                 hakn = TRUE)

# Age 
age_gen <- metagen(TE = mu_age_est,
                 seTE = mu_age_sd,
                 data = total_indep_var_results,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "ML",
                 hakn = TRUE)

# Educational level. This is now a dummy
edu_med_gen <- metagen(TE = mu_isced_med_est,
                 seTE = mu_isced_med_sd,
                 data = total_indep_var_results,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "ML",
                 hakn = TRUE)

edu_high_gen <- metagen(TE = mu_isced_high_est,
                 seTE = mu_isced_high_sd,
                 data = total_indep_var_results,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "ML",
                 hakn = TRUE)

# Extract all the data from the models and put them in a dataframe that will later be the input of the kable table
three_df <- data.frame(matrix(ncol = 5, nrow = 5))
colnames(three_df) <- c("mu_sigma_1", "Variable_1", "Estimate_1", "SE_1", "p_1")
three_df$mu_sigma_1 <- c("Mean attitudes", "", "", "", "")
three_df$Variable_1 <- c("Time", "Gender", "Age", "Isced intermediate (ref=basic)", "Isced advanced (ref=basic)")
three_df$Estimate_1 <- c(as.numeric(m2_att$b), gender_gen$TE.random, age_gen$TE.random, edu_med_gen$TE.random, edu_high_gen$TE.random)
three_df$SE_1 <- c(m2_att$se, gender_gen$seTE.random, age_gen$seTE.random, edu_med_gen$seTE.random, edu_high_gen$seTE.random)
three_df$p_1 <- c(m2_att$pval, gender_gen$pval.random, age_gen$pval.random, edu_med_gen$pval.random, edu_high_gen$pval.random)    

numeric_cols <- sapply(total_indep_var_results, is.numeric)

# Round only numeric columns to 9 decimals
total_indep_var_results[numeric_cols] <- lapply(total_indep_var_results[numeric_cols], function(x) round(x, 9))
                       
# The same for variance
m2_var <- rma(yi = sig_time_pred,
              sei = sig_time_sd_pred,
              data = total_reg_results,
              method = "ML",
              test = "knha")

# Gender
gender_var_gen <- metagen(TE = sig_sex_est,
                 seTE = sig_sex_sd,
                 data = total_indep_var_results,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "ML",
                 hakn = TRUE)

# Age
age_var_gen <- metagen(TE = sig_age_est,
                 seTE = sig_age_sd,
                 data = total_indep_var_results,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "ML",
                 hakn = TRUE)

# Education
edu_var_med_gen <- metagen(TE = sig_isced_med_est,
                 seTE = sig_isced_med_sd,
                 data = total_indep_var_results,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "ML",
                 hakn = TRUE)

edu_var_high_gen <- metagen(TE = sig_isced_high_est,
                 seTE = sig_isced_high_sd,
                 data = total_indep_var_results,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "ML",
                 hakn = TRUE)

four_df <- data.frame(matrix(ncol = 5, nrow = 5))
colnames(four_df) <- c("mu_sigma_1", "Variable_1", "Estimate_1", "SE_1", "p_1")
four_df$mu_sigma_1 <- c("Polarization attitudes", "", "", "", "")
four_df$Variable_1 <- c("Time", "Gender", "Age", "Isced intermediate (ref=basic)", "Isced advanced (ref=basic)")
four_df$Estimate_1 <- c(as.numeric(m2_var$b), gender_var_gen$TE.random, age_var_gen$TE.random, edu_var_med_gen$TE.random, edu_var_high_gen$TE.random)
four_df$SE_1 <- c(m2_att$se, gender_var_gen$seTE.random, age_var_gen$seTE.random, edu_var_med_gen$seTE.random, edu_var_high_gen$seTE.random)
four_df$p_1 <- c(m2_att$pval, gender_var_gen$pval.random, age_var_gen$pval.random, edu_var_med_gen$pval.random, edu_var_high_gen$pval.random)


# Bind rows of these two, these are all the pooled effects of the independent variables model
indep_df <- rbind(three_df, four_df)

#Now i want the interaction model as well
load("./data/meta_analysis/total_inter_results_new.RData")

# Delete outlier
total_inter_results <- subset(total_inter_results, subset = dep_var != "cc_unstop")

# First mean attitudes
m3_att <- rma(yi = mu_time_int,
              sei = mu_time_sd_int,
              data = total_reg_results,
              method = "ML",
              test = "knha")

# Gender 
gender_gen_int <- metagen(TE = mu_sex_est,
                 seTE = mu_sex_sd,
                 data = total_inter_results,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "ML",
                 hakn = TRUE)

# Age 
age_gen_int <- metagen(TE = mu_age_est,
                 seTE = mu_age_sd,
                 data = total_inter_results,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "ML",
                 hakn = TRUE)

# Educational level
edu_med_gen_int <- metagen(TE = mu_isced_med_est,
                 seTE = mu_isced_med_sd,
                 data = total_inter_results,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "ML",
                 hakn = TRUE)

edu_high_gen_int <- metagen(TE = mu_isced_high_est,
                 seTE = mu_isced_high_sd,
                 data = total_inter_results,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "ML",
                 hakn = TRUE)

# And the interaction effects 
# Gender 
gender_int_eff <- metagen(TE = mu_sex_est_inter,
                 seTE = mu_sex_sd_inter,
                 data = total_inter_results,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "ML",
                 hakn = TRUE)

# Age 
age_int_eff <- metagen(TE = mu_age_est_inter,
                 seTE = mu_age_sd_inter,
                 data = total_inter_results,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "ML",
                 hakn = TRUE)

# Educational level
edu_med_int_eff <- metagen(TE = mu_isced_med_est_inter,
                 seTE = mu_isced_med_sd_inter,
                 data = total_inter_results,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "ML",
                 hakn = TRUE)

edu_high_int_eff <- metagen(TE = mu_isced_high_est_inter,
                 seTE = mu_isced_high_sd_inter,
                 data = total_inter_results,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "ML",
                 hakn = TRUE)

# Now extract the data for a table
five_df <- data.frame(matrix(ncol = 5, nrow = 9))
colnames(five_df) <- c("mu_sigma_2", "Variable_2", "Estimate_2", "SE_2", "p_2")
five_df$mu_sigma_2 <- c("Mean attitudes", "", "", "", "", "", "", "", "")
five_df$Variable_2 <- c("Time", "Gender", "Age", "Isced intermediate (ref=basic)", "Isced advanced (ref=basic)", "Gender x time", "Age x time", "Isced intermediate x time", "Isced advanced x time")
five_df$Estimate_2 <- c(as.numeric(m3_att$b), gender_gen_int$TE.random, age_gen_int$TE.random, edu_med_gen_int$TE.random, edu_high_gen_int$TE.random, gender_int_eff$TE.random, age_int_eff$TE.random, edu_med_int_eff$TE.random, edu_high_int_eff$TE.random)
five_df$SE_2 <- c(m3_att$se, gender_gen_int$seTE.random, age_gen_int$seTE.random, edu_med_gen_int$seTE.random, edu_high_gen_int$seTE.random, gender_int_eff$seTE.random, age_int_eff$seTE.random, edu_med_int_eff$seTE.random, edu_high_int_eff$seTE.random)
five_df$p_2 <- c(m3_att$pval, gender_gen_int$pval.random, age_gen_int$pval.random, edu_med_gen_int$pval.random, edu_high_gen_int$pval.random, gender_int_eff$pval.random, age_int_eff$pval.random, edu_med_int_eff$pval.random, edu_high_int_eff$pval.random)

# Now the same procedure for the variance
m3_var <- rma(yi = sig_time_int_std,
              sei = sig_time_sd_int_std,
              data = total_reg_results,
              method = "ML",
              test = "knha")

# Gender 
gender_gen_int_var <- metagen(TE = sig_sex_est,
                 seTE = sig_sex_sd,
                 data = total_inter_results,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "ML",
                 hakn = TRUE)

# Age 
age_gen_int_var <- metagen(TE = sig_age_est,
                 seTE = sig_age_sd,
                 data = total_inter_results,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "ML",
                 hakn = TRUE)

# Educational level
edu_med_gen_int_var <- metagen(TE = sig_isced_med_est,
                 seTE = sig_isced_med_sd,
                 data = total_inter_results,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "ML",
                 hakn = TRUE)

edu_high_gen_int_var <- metagen(TE = sig_isced_high_est,
                 seTE = sig_isced_high_sd,
                 data = total_inter_results,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "ML",
                 hakn = TRUE)

# And the interaction effects 
# Gender 
gender_int_eff_var <- metagen(TE = sig_sex_est_inter,
                 seTE = sig_sex_sd_inter,
                 data = total_inter_results,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "ML",
                 hakn = TRUE)

# Age 
age_int_eff_var <- metagen(TE = sig_age_est_inter,
                 seTE = sig_age_sd_inter,
                 data = total_inter_results,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "ML",
                 hakn = TRUE)

# Educational level
edu_med_int_eff_var <- metagen(TE = sig_isced_med_est_inter,
                 seTE = sig_isced_med_sd_inter,
                 data = total_inter_results,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "ML",
                 hakn = TRUE)

edu_high_int_eff_var <- metagen(TE = sig_isced_high_est_inter,
                 seTE = sig_isced_high_sd_inter,
                 data = total_inter_results,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "ML",
                 hakn = TRUE)

six_df <- data.frame(matrix(ncol = 5, nrow = 9))
colnames(six_df) <- c("mu_sigma_2", "Variable_2", "Estimate_2", "SE_2", "p_2")
six_df$mu_sigma_2 <- c("Polarization attitudes", "", "", "", "", "", "", "", "")
six_df$Variable_2 <- c("Time", "Gender", "Age", "Isced intermediate (ref=basic)", "Isced advanced (ref=basic)", "Gender x time", "Age x time", "Isced intermediate x time", "Isced advanced x time")
six_df$Estimate_2 <- c(as.numeric(m3_var$b), gender_gen_int_var$TE.random, age_gen_int_var$TE.random, edu_med_gen_int_var$TE.random, edu_high_gen_int_var$TE.random, gender_int_eff_var$TE.random, age_int_eff_var$TE.random, edu_med_int_eff_var$TE.random, edu_high_int_eff_var$TE.random)
six_df$SE_2 <- c(m3_var$se, gender_gen_int_var$seTE.random, age_gen_int_var$seTE.random, edu_med_gen_int_var$seTE.random, edu_high_gen_int_var$seTE.random, gender_int_eff_var$seTE.random, age_int_eff_var$seTE.random, edu_med_int_eff_var$seTE.random, edu_high_int_eff_var$seTE.random)
six_df$p_2 <- c(m3_att$pval, gender_gen_int_var$pval.random, age_gen_int_var$pval.random, edu_med_gen_int_var$pval.random, edu_high_gen_int_var$pval.random, gender_int_eff_var$pval.random, age_int_eff_var$pval.random, edu_med_int_eff_var$pval.random, edu_high_int_eff_var$pval.random)

#Bind these two, this now has all the pooled effects of the interaction effects
inter_df <- rbind(five_df, six_df)
```

```{r, eval=FALSE}
#Columnbind the three datasets
# Difficult to columnbind them, because they're of different lengths (logically)
df_list <- list(empty_df, indep_df, inter_df)

bind_cols_fill <- function(df_list) {

  max_rows <- map_int(df_list, nrow) %>% max()
  
  map(df_list, function(df) {
    if(nrow(df) == max_rows) return(df)
    first <- names(df)[1] %>% sym()
    df %>% add_row(!!first := rep(NA, max_rows - nrow(df)))
  }) %>% bind_cols()
}

total_df <- bind_cols_fill(df_list)

#Change the order a bit, just like in the previous table 
write_xlsx(total_df,  "./data/descriptives/kable_model_all_pooled_effects.xlsx" )
```


```{r, warning=FALSE}
model_new <- read_excel("./data/descriptives/kable_model_all_pooled_effects.xlsx" )

# I Want to round the numeric variables to 3 decimals
model_new <- dplyr::mutate(model_new, across(.cols = c(-mu_sigma_2, -Variable_2), .fns = as.numeric))
numeric_cols <- sapply(model_new, is.numeric)
model_new[, numeric_cols] <- round(model_new[, numeric_cols], digits = 3)

# Create a new variable to use stars instead of the full p-values in the table
model_new$p_text <- case_when(
  model_new$p >= 0.05 ~ "",
model_new$p < 0.001 ~ "***",
model_new$p < 0.01 ~ "**",
model_new$p < 0.05 ~ "*"
)

model_new$p_text_1 <- case_when(
  model_new$p_1 >= 0.05 ~ "",
model_new$p_1 < 0.001 ~ "***",
model_new$p_1 < 0.01 ~ "**",
model_new$p_1 < 0.05 ~ "*"
)

model_new$p_text_2 <- case_when(
  model_new$p_2 >= 0.05 ~ "",
model_new$p_2 < 0.001 ~ "***",
model_new$p_2 < 0.01 ~ "**",
model_new$p_2 < 0.05 ~ "*"
)

# Now only select the variables that I want to show in the table
model_new <- dplyr::select(model_new, mu_sigma_2, Variable_2, Estimate, SE, p_text, Estimate_1, SE_1, p_text_1, Estimate_2, SE_2, p_text_2)

# Make and save the table as html file
kable(model_new, digits = 3, caption = "Table 3. All pooled effects mean attitudes and polarization", 
      col.names = c( "", "Variables", "Estimate", "Std. Error", "", "Estimate", "Std. Error", "", "Estimate", "Std. Error", "")) %>%
  kable_classic_2(html_font = "Times", fixed_thead = T, full_width = F) %>%
  add_header_above(c(" " = 2, "Time-only model" = 3, "Indepent var model" = 3, "Interaction model" = 3)) %>%
   footnote(
    general_title = "Note.",
    general = "*** = p < 0.001, ** = p < 0.01, * = p < 0.05",
    threeparttable = TRUE,
    footnote_as_chunk = TRUE
    ) %>%
    save_kable("./output/pooled_effects_table_FEB_without_outlier.html")
```
