---
title: "Climate change attitudes and polarization"
author: "by: Anuschka Peelen"
output: rmarkdown::html_document


---

```{r, install remotely, globalsettings, echo=FALSE, warning=FALSE, results='hide', eval=FALSE}
install.packages("remotes")
remotes::install_github("rlesur/klippy")
install.packages("servr")
library(servr)
servr::httw()
```

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()

colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }

```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
klippy::klippy(color = 'darkred')
klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

------------------------------------------------------------------------

::: columns
::: {.column width="50%"}
# Trends in climate change

Last compiled on `r format(Sys.time(), '%B, %Y')`

\*\* <br>

------------------------------------------------------------------------
:::

::: {.column width="50%"}

:::
:::


## Welcome
Welcome to the replication website that comes with the article on climate change attitudes and polarization, based on my thesis. 

## How to use this website

In the top menu, you can navigate through different parts of this project. Under "scripts" you will find all the scripts to replicate the data preparation and analyses of this thesis yourself. Under "blog" you will find the blog post accompanying this thesis (in Dutch). 


