---
title: "Gamlss regressions all datasets"
author: "Anuschka Peelen"
date: "`r Sys.Date()`"
output: html_document
---

```{r, echo=FALSE}
knitr::opts_chunk$set(eval = FALSE)
knitr::opts_chunk$set(number_sections = FALSE)
options(width = 100)
colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }
```

```{css, echo=FALSE}
pre {
  max-height: 300px;
  overflow-y: auto;
}

pre[class] {
  max-height: 100px;
}
```

In this script I use loops to perform gamlss regressions for all 71 attitudes. The lists that I will get as output are saved with all the information, after which - in another script - i will extract the raw effects sizes used as input for the meta-regressions. In this script, rather than putting time to 0, i use actual surveyyears as input.  

```{r}
rm(list = ls())
library(gamlss)
library(tidyverse)
library(dplyr)
library(fastDummies)
```

## ESS {-}

```{r}
load("./data/final_data/esstotal.RData")

# Gamlss cannot handle NAs, so I have to listwise delete all of them
ess_complete <- esstotal %>% drop_na()

# I want to build models. In the empty model, I only want to include surveyyear. 
predictors <- c("surveyyear")
deps <- c("worry", "cause", "pers_resp")

ess_list_empty <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression. The sigma formula pastes every variable one by one and calculates variance, the other formula shows the mean attitudes effects
  ess_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula,  family=NO(mu.link = "identity", sigma.link = "identity"), data = ess_complete, weights = weightvec)
  
  ess_list_empty[[i]] <- ess_fit
} 


summary(ess_list_empty[[1]]) #Sig pos effect of surveyyear on both intercept and variance (worry)
summary(ess_list_empty[[2]]) # Sig neg effect on intercept, sig pos effect on variance (cause)
summary(ess_list_empty[[3]]) # Sig pos effect on intercept, sig neg effect on variance (pers_resp)

 
save(ess_list_empty, file="./data/final_data/regression_outputs/ess_list_empty_srvy.RData")

#Estimate a second model with the indicators + time
predictors <- c("surveyyear", "sex", "isced_cat", "age")
deps <- c("worry", "cause", "pers_resp")

ess_list_preds <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  ess_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = ess_complete, weights = weightvec)
  
  ess_list_preds[[i]] <- ess_fit
} 

summary(ess_list_preds[[1]]) 

save(ess_list_preds, file="./data/final_data/regression_outputs/ess_list_preds_w_srvy.RData")

#Now the last model with interaction of time on predictor variables
ess_complete$age_time <- ess_complete$age * ess_complete$surveyyear
ess_complete$sex_time <- as.numeric(ess_complete$sex) * ess_complete$surveyyear
ess_complete <- fastDummies::dummy_cols(ess_complete, select_columns = "isced_cat")
ess_complete$isced_basic_time <- ess_complete$isced_cat_Basic * ess_complete$surveyyear
ess_complete$isced_intermediate_time <- ess_complete$isced_cat_Intermediate * ess_complete$surveyyear
ess_complete$isced_advanced_time <- ess_complete$isced_cat_Advanced * ess_complete$surveyyear

interactions <- c("age_time", "sex_time", "isced_intermediate_time", "isced_advanced_time")

ess_list_interactions <- list()

 for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = " + ")))
  # Perform the linear regression
  ess_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = "+ "))), sigma.formula = sigma.formula," + ", family=NO(mu.link = "identity", sigma.link = "identity"), data = ess_complete, weights = weightvec)
  
  ess_list_interactions[[i]] <- ess_fit
} 


summary(ess_list_interactions[[1]]) 
summary(ess_list_interactions[[2]]) 
summary(ess_list_interactions[[3]])

save(ess_list_interactions, file="./data/final_data/regression_outputs/ess_list_interactions_w_srvy.RData")
```

## EVS {-}

```{r}
# Perform the same procedure for the EVS
rm(list=ls())
load("./data/final_data/evssel.RData")

evs_complete <- evssel %>% dplyr::select(surveyyear:marstat, weightvec, isced_cat)
evs_complete <- evs_complete %>% drop_na()

predictors <- c("surveyyear")
deps <- c("climate5")

evs_list_empty <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regrevsion
  evs_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = evs_complete, weights = weightvec)
  
  evs_list_empty[[i]] <- evs_fit
} 

summary(evs_list_empty[[1]]) 

model1 <- evs_list_empty[[1]]

save(evs_list_empty, file="./data/final_data/regression_outputs/evs_list_empty_w_srvy.RData")

# Predictor model
predictors <- c("surveyyear", "sex", "isced_cat", "age")
deps <- c("climate5")

evs_list_preds <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regrevsion
  evs_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = evs_complete, weights = weightvec)
  
  evs_list_preds[[i]] <- evs_fit
} 

summary(evs_list_preds[[1]]) 

save(evs_list_preds, file="./data/final_data/regression_outputs/evs_list_preds_w_srvy.RData")

#Now the last model with interaction of time on predictor variables
evs_complete$age_time <- evs_complete$age * evs_complete$surveyyear
evs_complete$sex_time <- as.numeric(evs_complete$sex) * evs_complete$surveyyear
evs_complete <- fastDummies::dummy_cols(evs_complete, select_columns = "isced_cat")
evs_complete$isced_basic_time <- evs_complete$isced_cat_Basic * evs_complete$surveyyear
evs_complete$isced_intermediate_time <- evs_complete$isced_cat_Intermediate * evs_complete$surveyyear
evs_complete$isced_advanced_time <- evs_complete$isced_cat_Advanced * evs_complete$surveyyear

interactions <- c("age_time", "sex_time", "isced_intermediate_time", "isced_advanced_time")

evs_list_interactions <- list()

 for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = " + ")))
  # Perform the linear regrevsion
  evs_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = "+ "))), sigma.formula = sigma.formula," + ", family=NO(mu.link = "identity", sigma.link = "identity"), data = evs_complete, weights = weightvec)
  
  evs_list_interactions[[i]] <- evs_fit
} 

summary(evs_list_interactions[[1]]) 

save(evs_list_interactions, file="./data/final_data/regression_outputs/evs_list_interactions_w_srvy.RData")

```

## I&O {-}

```{r}
rm(list=ls())
load("./data/final_data/io_total.RData")
io_complete <- io_total %>% dplyr::select(worried:surveyyear, weightvec, isced_cat)
#Urban, IOINKOMEN, IOPOL has to go away
io_complete = subset(io_complete, select = -c(urban,IOINKOMEN, IOPOL2017) )
io_complete <- io_complete %>% drop_na()


predictors <- c("surveyyear")
deps <- c("worried", "frontrunner", "worry_future", "resp_citiz", "dk_start", "do_gov", "buss_help", "min_contr", "human_resp")

io_list_empty <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  io_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = io_complete, weights = weightvec)
  
  io_list_empty[[i]] <- io_fit
} 

summary(io_list_empty[[1]]) 
summary(io_list_empty[[2]])


save(io_list_empty, file="./data/final_data/regression_outputs/io_list_empty_srvy.RData")

# Predictor model
predictors <- c("surveyyear", "sex", "isced_cat", "age")
deps <- c("worried", "frontrunner", "worry_future", "resp_citiz", "dk_start", "do_gov", "buss_help", "min_contr", "human_resp")

io_list_preds <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  io_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = io_complete, weights = weightvec)
  
  io_list_preds[[i]] <- io_fit
} 

summary(io_list_preds[[1]]) 

save(io_list_preds, file="./data/final_data/regression_outputs/io_list_preds_w_srvy.RData")

#Now the last model with interaction of time on predictor variables
io_complete$age_time <- io_complete$age * io_complete$surveyyear
io_complete$sex_time <- as.numeric(io_complete$sex) * io_complete$surveyyear
io_complete <- fastDummies::dummy_cols(io_complete, select_columns = "isced_cat")
io_complete$isced_basic_time <- io_complete$isced_cat_Basic * io_complete$surveyyear
io_complete$isced_intermediate_time <- io_complete$isced_cat_Intermediate * io_complete$surveyyear
io_complete$isced_advanced_time <- io_complete$isced_cat_Advanced * io_complete$surveyyear

interactions <- c("age_time", "sex_time", "isced_intermediate_time", "isced_advanced_time")

io_list_interactions <- list()

 for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = " + ")))
  # Perform the linear regression
  io_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = "+ "))), sigma.formula = sigma.formula," + ", family=NO(mu.link = "identity", sigma.link = "identity"), data = io_complete, weights = weightvec)
  
  io_list_interactions[[i]] <- io_fit
} 


summary(io_list_interactions[[1]]) 

save(io_list_interactions, file="./data/final_data/regression_outputs/io_list_interactions_w_srvy.RData")

```

## ISSP {-}

```{r}
rm(list=ls())
load("./data/final_data/issptotal.Rdata")
issptotal$surveyyear[is.na(issptotal$surveyyear)] <- "2010"
issptotal$surveyyear <- as.numeric(issptotal$surveyyear)

# The issp has variables that are asked in all three waves, and variables that are asked only in 2 waves. So I have to run the code on subsets of the data. First I estimate the models for the statements that are asked throughout the three waves
issp_complete <- issptotal %>% dplyr::select(surveyyear:marstat, weightvec, isced_cat)
issp_complete <- issp_complete %>% drop_na()

# Time-only
predictors <- c("surveyyear")
deps <- c("worry", "lifeharm", "willing_price", "willing_tax", "willing_living", "do_right", "progharm", "econprotect", "people_decide")

issp_list_empty <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  issp_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula,
                     family=NO(mu.link = "identity", sigma.link = "identity"), data = issp_complete, weights = weightvec)
  
  issp_list_empty[[i]] <- issp_fit
} 

summary(issp_list_empty[[1]]) 
summary(issp_list_empty[[2]]) 
summary(issp_list_empty[[3]]) 
 
save(issp_list_empty, file="./data/final_data/regression_outputs/issp_list_empty_w_srvy.RData")

# Now with predictors
predictors <- c("surveyyear", "sex", "isced_cat", "age")
deps <- c("worry", "lifeharm", "willing_price", "willing_tax", "willing_living", "do_right", "progharm", "econprotect", "people_decide" )

issp_list_preds <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  issp_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula,
                      family=NO(mu.link = "identity", sigma.link = "identity"), data = issp_complete, weights = weightvec)
  
  issp_list_preds[[i]] <- issp_fit
} 


save(issp_list_preds, file="./data/final_data/regression_outputs/issp_list_preds_w_srvy.RData")

# And now interactions
issp_complete$age_time <- issp_complete$age * issp_complete$surveyyear
issp_complete$sex_time <- as.numeric(issp_complete$sex) * issp_complete$surveyyear
issp_complete <- fastDummies::dummy_cols(issp_complete, select_columns = "isced_cat")
issp_complete$isced_basic_time <- issp_complete$isced_cat_Basic * issp_complete$surveyyear
issp_complete$isced_intermediate_time <- issp_complete$isced_cat_Intermediate * issp_complete$surveyyear
issp_complete$isced_advanced_time <- issp_complete$isced_cat_Advanced * issp_complete$surveyyear

interactions <- c("age_time", "sex_time", "isced_intermediate_time", "isced_advanced_time")

issp_list_interactions <- list()

 for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = " + ")))
  # Perform the linear regressisspn
  issp_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = "+ "))), sigma.formula = sigma.formula," + ", family=NO(mu.link = "identity", sigma.link = "identity"), data = issp_complete, weights = weightvec)
  
  issp_list_interactions[[i]] <- issp_fit
} 

save(issp_list_interactions, file="./data/final_data/regression_outputs/issp_list_interactions_w_srvy.RData")

# Now the variables that are only asked twice
issp_complete <- issptotal %>% dplyr::select(surveyyear, isced:growharm, weightvec, isced_cat)
issp_complete <- issp_complete %>% drop_na()

# Time-only model
predictors <- c("surveyyear")
deps <- c("exag", "moreimp", "othersame", "country_effort", "growharm")

issp_list_empty_2_waves <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  issp_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = issp_complete, weights = weightvec)
  
  issp_list_empty_2_waves[[i]] <- issp_fit
  } 
 

save(issp_list_empty_2_waves, file="./data/final_data/regression_outputs/issp_list_empty_2_waves_w_srvy.RData")

# And the model with the predictors
predictors <- c("surveyyear", "sex", "isced_cat", "age")
deps <- c("exag", "moreimp", "othersame", "country_effort", "growharm")

issp_list_preds_2_waves <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  issp_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = issp_complete, weights = weightvec)
  
  issp_list_preds_2_waves[[i]] <- issp_fit
} 

summary(issp_list_preds_2_waves[[1]]) 

save(issp_list_preds_2_waves, file="./data/final_data/regression_outputs/issp_list_preds_2_waves_w_srvy.RData")

# And lastly, again the interactions
issp_complete$age_time <- issp_complete$age * issp_complete$surveyyear
issp_complete$sex_time <- as.numeric(issp_complete$sex) * issp_complete$surveyyear
issp_complete <- fastDummies::dummy_cols(issp_complete, select_columns = "isced_cat")
issp_complete$isced_basic_time <- issp_complete$isced_cat_Basic * issp_complete$surveyyear
issp_complete$isced_intermediate_time <- issp_complete$isced_cat_Intermediate * issp_complete$surveyyear
issp_complete$isced_advanced_time <- issp_complete$isced_cat_Advanced * issp_complete$surveyyear

interactions <- c("age_time", "sex_time", "isced_intermediate_time", "isced_advanced_time")

issp_list_interactions_2_waves <- list()

 for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = " + ")))
  # Perform the linear regressisspn
  issp_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = "+ "))), sigma.formula = sigma.formula," + ", family=NO(mu.link = "identity", sigma.link = "identity"), data = issp_complete, weights = weightvec)
  
  issp_list_interactions_2_waves[[i]] <- issp_fit
} 

save(issp_list_interactions_2_waves, file="./data/final_data/regression_outputs/issp_list_interactions_2_waves_w_srvy.RData")
```

## EB {-}

```{r}
rm(list=ls())
# Now the most difficult one: Eurobarometer. No items are asked steadily throughout time, so have to work with a lot of subsets. 
load("./data/final_data/eb_tot.Rdata")

# first 1986 - 1995
eb_complete <- eb_tot %>% dplyr::select(surveyyear, env_ec_stat, env_prsimp, sex, isced: urban, weightvec, isced_cat)
# Religion is only asked in one wave
eb_complete <- eb_complete %>% drop_na()


# First empty model 
predictors <- c("surveyyear")
deps <- c("env_ec_stat", "env_prsimp")

eb_list_empty_1986 <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula,
                   family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_empty_1986[[i]] <- eb_fit
} 


save(eb_list_empty_1986, file="./data/final_data/regression_outputs/eb_list_empty_1986_w_srvy.RData")

# Model with predictors
predictors <- c("surveyyear", "sex", "isced_cat", "age")
deps <- c("env_ec_stat", "env_prsimp")

eb_list_preds_1986 <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula,
                   family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_preds_1986[[i]] <- eb_fit
} 

save(eb_list_preds_1986, file="./data/final_data/regression_outputs/eb_list_preds_1986_w_new_srvy.RData")

# And the model with interactions
eb_complete$age_time <- eb_complete$age * eb_complete$surveyyear
eb_complete$sex_time <- as.numeric(eb_complete$sex) * eb_complete$surveyyear
eb_complete <- fastDummies::dummy_cols(eb_complete, select_columns = "isced_cat")
eb_complete$isced_basic_time <- eb_complete$isced_cat_Basic * eb_complete$surveyyear
eb_complete$isced_intermediate_time <- eb_complete$isced_cat_Intermediate * eb_complete$surveyyear
eb_complete$isced_advanced_time <- eb_complete$isced_cat_Advanced * eb_complete$surveyyear

interactions <- c("age_time", "sex_time", "isced_intermediate_time", "isced_advanced_time")

eb_list_interactions_1986 <- list()

 for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = "+ "))), sigma.formula = sigma.formula," + ", family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_interactions_1986[[i]] <- eb_fit
} 

save(eb_list_interactions_1986, file="./data/final_data/regression_outputs/eb_list_interactions_1986_w_srvy.RData")
```

```{r}
# Now with the influence of environment on quality of life
eb_complete <- eb_tot %>% dplyr::select(surveyyear, env_quallife, sex, isced, urban, age, weightvec, isced_cat)
# Lrplace and income are not asked in all waves
eb_complete <- eb_complete %>% drop_na()

# First empty model 
predictors <- c("surveyyear")
deps <- c("env_quallife")

eb_list_empty_quallife <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_empty_quallife[[i]] <- eb_fit
} 

summary(eb_list_empty_quallife[[1]]) 

save(eb_list_empty_quallife, file="./data/final_data/regression_outputs/eb_list_empty_quallife_w_srvy.RData")

# Model with predictors
predictors <- c("surveyyear", "sex", "isced_cat", "age")
deps <- c("env_quallife")

eb_list_preds_quallife <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula,
                   family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_preds_quallife[[i]] <- eb_fit
} 



save(eb_list_preds_quallife, file="./data/final_data/regression_outputs/eb_list_preds_quallife_w_srvy.RData")

# And the model with interactions
eb_complete$age_time <- eb_complete$age * eb_complete$surveyyear
eb_complete$sex_time <- as.numeric(eb_complete$sex) * eb_complete$surveyyear
eb_complete <- fastDummies::dummy_cols(eb_complete, select_columns = "isced_cat")
eb_complete$isced_basic_time <- eb_complete$isced_cat_Basic * eb_complete$surveyyear
eb_complete$isced_intermediate_time <- eb_complete$isced_cat_Intermediate * eb_complete$surveyyear
eb_complete$isced_advanced_time <- eb_complete$isced_cat_Advanced * eb_complete$surveyyear


interactions <- c("age_time", "sex_time", "isced_intermediate_time", "isced_advanced_time")

eb_list_interactions_quallife <- list()

 for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = " + ")))
  # Perform the linear regressebn
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = "+ "))), sigma.formula = sigma.formula," + ", family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_interactions_quallife[[i]] <- eb_fit
} 

summary(eb_list_interactions_quallife[[1]]) 

save(eb_list_interactions_quallife, file="./data/final_data/regression_outputs/eb_list_interactions_quallife_w_srvy.RData")
```

```{r}
# Now 2 statements that are asked 4 times
eb_complete <- eb_tot %>% dplyr::select(surveyyear, role_ind, big_pol, sex, isced, urban, age, weightvec, isced_cat)
# Lrplace and income are not asked in all waves
eb_complete <- eb_complete %>% drop_na()

# First empty model 
predictors <- c("surveyyear")
deps <- c("role_ind", "big_pol")

eb_list_empty_2007 <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_empty_2007[[i]] <- eb_fit
} 

summary(eb_list_empty_2007[[2]]) 

save(eb_list_empty_2007, file="./data/final_data/regression_outputs/eb_list_empty_2007_w_srvy.RData")

# Model with predictors
predictors <- c("surveyyear", "sex", "isced_cat", "age")
deps <- c("role_ind", "big_pol")

eb_list_preds_2007 <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_preds_2007[[i]] <- eb_fit
} 

summary(eb_list_preds_2007[[1]]) 

save(eb_list_preds_2007, file="./data/final_data/regression_outputs/eb_list_preds_2007_w_new_srvy.RData")

# And the model with interactions
eb_complete$age_time <- eb_complete$age * eb_complete$surveyyear
eb_complete$sex_time <- as.numeric(eb_complete$sex) * eb_complete$surveyyear
eb_complete <- fastDummies::dummy_cols(eb_complete, select_columns = "isced_cat")
eb_complete$isced_basic_time <- eb_complete$isced_cat_Basic * eb_complete$surveyyear
eb_complete$isced_intermediate_time <- eb_complete$isced_cat_Intermediate * eb_complete$surveyyear
eb_complete$isced_advanced_time <- eb_complete$isced_cat_Advanced * eb_complete$surveyyear


interactions <- c("age_time", "sex_time", "isced_intermediate_time", "isced_advanced_time")

eb_list_interactions_2007 <- list()

 for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = " + ")))
  # Perform the linear regressebn
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = "+ "))), sigma.formula = sigma.formula," + ", family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_interactions_2007[[i]] <- eb_fit
} 

summary(eb_list_interactions_2007[[1]]) 

save(eb_list_interactions_2007, file="./data/final_data/regression_outputs/eb_list_interactions_2007_w_srvy.RData")
```

```{r}
# Now 2 statements that are asked 4 times
eb_complete <- eb_tot %>% dplyr::select(surveyyear, buyprod, sex, isced, urban, age, weightvec, isced_cat)
eb_complete <- eb_complete %>% drop_na()


# First empty model 
predictors <- c("surveyyear")
deps <- c("buyprod")

eb_list_empty_buyprod <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_empty_buyprod[[i]] <- eb_fit
} 

summary(eb_list_empty_buyprod[[1]]) 

save(eb_list_empty_buyprod, file="./data/final_data/regression_outputs/eb_list_empty_buyprod_w_srvy.RData")

# Model with predictors
predictors <- c("surveyyear", "sex", "isced_cat", "age")
deps <- c("buyprod")

eb_list_preds_buyprod <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_preds_buyprod[[i]] <- eb_fit
} 

summary(eb_list_preds_buyprod[[1]]) 

save(eb_list_preds_buyprod, file="./data/final_data/regression_outputs/eb_list_preds_buyprod_w_srvy.RData")

# And the model with interactions
eb_complete$age_time <- eb_complete$age * eb_complete$surveyyear
eb_complete$sex_time <- as.numeric(eb_complete$sex) * eb_complete$surveyyear
eb_complete <- fastDummies::dummy_cols(eb_complete, select_columns = "isced_cat")
eb_complete$isced_basic_time <- eb_complete$isced_cat_Basic * eb_complete$surveyyear
eb_complete$isced_intermediate_time <- eb_complete$isced_cat_Intermediate * eb_complete$surveyyear
eb_complete$isced_advanced_time <- eb_complete$isced_cat_Advanced * eb_complete$surveyyear


interactions <- c("age_time", "sex_time", "isced_intermediate_time", "isced_advanced_time")

eb_list_interactions_buyprod <- list()

 for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = "+ "))), sigma.formula = sigma.formula," + ", family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_interactions_buyprod[[i]] <- eb_fit
} 


save(eb_list_interactions_buyprod, file="./data/final_data/regression_outputs/eb_list_interactions_buyprod_w_srvy.RData")
```

```{r}
# Now 2 statements that are asked 4 times
eb_complete <- eb_tot %>% dplyr::select(surveyyear, eff_daily, sex, isced, urban, age, weightvec, isced_cat)
eb_complete <- eb_complete %>% drop_na()


# First empty model 
predictors <- c("surveyyear")
deps <- c("eff_daily")

eb_list_empty_eff_daily <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_empty_eff_daily[[i]] <- eb_fit
} 

summary(eb_list_empty_eff_daily[[1]]) 

save(eb_list_empty_eff_daily, file="./data/final_data/regression_outputs/eb_list_empty_eff_daily_w_srvy.RData")

# Model with predictors
predictors <- c("surveyyear", "sex", "isced_cat", "age")
deps <- c("eff_daily")

eb_list_preds_eff_daily <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_preds_eff_daily[[i]] <- eb_fit
} 

summary(eb_list_preds_eff_daily[[1]]) 

save(eb_list_preds_eff_daily, file="./data/final_data/regression_outputs/eb_list_preds_eff_daily_w_srvy.RData")

# And the model with interactions
eb_complete$age_time <- eb_complete$age * eb_complete$surveyyear
eb_complete$sex_time <- as.numeric(eb_complete$sex) * eb_complete$surveyyear
eb_complete <- fastDummies::dummy_cols(eb_complete, select_columns = "isced_cat")
eb_complete$isced_basic_time <- eb_complete$isced_cat_Basic * eb_complete$surveyyear
eb_complete$isced_intermediate_time <- eb_complete$isced_cat_Intermediate * eb_complete$surveyyear
eb_complete$isced_advanced_time <- eb_complete$isced_cat_Advanced * eb_complete$surveyyear


interactions <- c("age_time", "sex_time", "isced_intermediate_time", "isced_advanced_time")

eb_list_interactions_eff_daily <- list()

 for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = "+ "))), sigma.formula = sigma.formula," + ", family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_interactions_eff_daily[[i]] <- eb_fit
} 


save(eb_list_interactions_eff_daily, file="./data/final_data/regression_outputs/eb_list_interactions_eff_daily_w_srvy.RData")
```

```{r}
# Now 4 vars that are asked 2 waves
eb_complete <- eb_tot %>% dplyr::select(surveyyear, cc_unstop:cc_prsact, sex, isced, urban, age, weightvec, isced_cat)
eb_complete <- eb_complete %>% drop_na()

# First empty model 
predictors <- c("surveyyear")
deps <- c("cc_unstop", "cc_exag", "cc_poseu", "cc_prsact")

eb_list_empty_2008 <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_empty_2008[[i]] <- eb_fit
} 


save(eb_list_empty_2008, file="./data/final_data/regression_outputs/eb_list_empty_2008_w_srvy.RData")

# Model with predictors
predictors <- c("surveyyear", "sex", "isced_cat", "age")
deps <- c("cc_unstop", "cc_exag", "cc_poseu", "cc_prsact")

eb_list_preds_2008 <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_preds_2008[[i]] <- eb_fit
} 


save(eb_list_preds_2008, file="./data/final_data/regression_outputs/eb_list_preds_2008_w_srvy.RData")

# And the model with interactions
eb_complete$age_time <- eb_complete$age * eb_complete$surveyyear
eb_complete$sex_time <- as.numeric(eb_complete$sex) * eb_complete$surveyyear
eb_complete <- fastDummies::dummy_cols(eb_complete, select_columns = "isced_cat")
eb_complete$isced_basic_time <- eb_complete$isced_cat_Basic * eb_complete$surveyyear
eb_complete$isced_intermediate_time <- eb_complete$isced_cat_Intermediate * eb_complete$surveyyear
eb_complete$isced_advanced_time <- eb_complete$isced_cat_Advanced * eb_complete$surveyyear


interactions <- c("age_time", "sex_time", "isced_intermediate_time", "isced_advanced_time")

eb_list_interactions_2008 <- list()

 for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = "+ "))), sigma.formula = sigma.formula," + ", family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_interactions_2008[[i]] <- eb_fit
} 


save(eb_list_interactions_2008, file="./data/final_data/regression_outputs/eb_list_interactions_2008_w_srvy.RData")
```


```{r}
# Climate change perception asked in six waves
eb_complete <- eb_tot %>% dplyr::select(surveyyear, ccpercept, cchange, sex, isced, urban, age, weightvec, isced_cat)
eb_complete <- eb_complete %>% drop_na()


# First empty model 
predictors <- c("surveyyear")
deps <- c("ccpercept", "cchange")

eb_list_empty_2009 <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_empty_2009[[i]] <- eb_fit
} 

save(eb_list_empty_2009, file="./data/final_data/regression_outputs/eb_list_empty_2009_w_srvy.RData")

# Model with predictors
predictors <- c("surveyyear", "sex", "isced_cat", "age")
deps <- c("ccpercept", "cchange")

eb_list_preds_2009 <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_preds_2009[[i]] <- eb_fit
} 


save(eb_list_preds_2009, file="./data/final_data/regression_outputs/eb_list_preds_2009_w_new_srvy.RData")

# And the model with interactions
eb_complete$age_time <- eb_complete$age * eb_complete$surveyyear
eb_complete$sex_time <- as.numeric(eb_complete$sex) * eb_complete$surveyyear
eb_complete <- fastDummies::dummy_cols(eb_complete, select_columns = "isced_cat")
eb_complete$isced_basic_time <- eb_complete$isced_cat_Basic * eb_complete$surveyyear
eb_complete$isced_intermediate_time <- eb_complete$isced_cat_Intermediate * eb_complete$surveyyear
eb_complete$isced_advanced_time <- eb_complete$isced_cat_Advanced * eb_complete$surveyyear


interactions <- c("age_time", "sex_time", "isced_intermediate_time", "isced_advanced_time")

eb_list_interactions_2009 <- list()

 for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = "+ "))), sigma.formula = sigma.formula," + ", family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_interactions_2009[[i]] <- eb_fit
} 

summary(eb_list_interactions_2009[[1]]) 

save(eb_list_interactions_2009, file="./data/final_data/regression_outputs/eb_list_interactions_2009_w_srvy.RData")
```

```{r}
# Personal importance asked in 3 waves
eb_complete <- eb_tot %>% dplyr::select(surveyyear, pers_imp, sex, isced, urban, age, weightvec, isced_cat)
eb_complete <- eb_complete %>% drop_na()

# First empty model 
predictors <- c("surveyyear")
deps <- c("pers_imp")

eb_list_empty_pers_imp <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula,family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_empty_pers_imp[[i]] <- eb_fit
} 

save(eb_list_empty_pers_imp, file="./data/final_data/regression_outputs/eb_list_empty_pers_imp_w_srvy.RData")

# Model with predictors
predictors <- c("surveyyear", "sex", "isced_cat", "age")
deps <- c("pers_imp")

eb_list_preds_pers_imp <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula,
                   family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_preds_pers_imp[[i]] <- eb_fit
} 


save(eb_list_preds_pers_imp, file="./data/final_data/regression_outputs/eb_list_preds_pers_imp_w_srvy.RData")

# And the model with interactions
eb_complete$age_time <- eb_complete$age * eb_complete$surveyyear
eb_complete$sex_time <- as.numeric(eb_complete$sex) * eb_complete$surveyyear
eb_complete <- fastDummies::dummy_cols(eb_complete, select_columns = "isced_cat")
eb_complete$isced_basic_time <- eb_complete$isced_cat_Basic * eb_complete$surveyyear
eb_complete$isced_intermediate_time <- eb_complete$isced_cat_Intermediate * eb_complete$surveyyear
eb_complete$isced_advanced_time <- eb_complete$isced_cat_Advanced * eb_complete$surveyyear


interactions <- c("age_time", "sex_time", "isced_intermediate_time", "isced_advanced_time")

eb_list_interactions_pers_imp <- list()

 for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = "+ "))), sigma.formula = sigma.formula," + ", family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_interactions_pers_imp[[i]] <- eb_fit
} 


save(eb_list_interactions_pers_imp, file="./data/final_data/regression_outputs/eb_list_interactions_pers_imp_w_srvy.RData")
```

```{r}
# Questions about who does enough asked in 3 waves
eb_complete <- eb_tot %>% dplyr::select(surveyyear, doprot_natgov:doprot_citiz, sex, isced, urban, age, weightvec, isced_cat)
eb_complete <- eb_complete %>% drop_na()

# First empty model 
predictors <- c("surveyyear")
deps <- c("doprot_natgov", "doprot_eu", "doprot_region", "doprot_comp", "doprot_citiz")

eb_list_empty_doprot <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_empty_doprot[[i]] <- eb_fit
} 


save(eb_list_empty_doprot, file="./data/final_data/regression_outputs/eb_list_empty_doprot_w_srvy.RData")

# Model with predictors
predictors <- c("surveyyear", "sex", "isced_cat", "age")
deps <- c("doprot_natgov", "doprot_eu", "doprot_region", "doprot_comp", "doprot_citiz")

eb_list_preds_doprot <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_preds_doprot[[i]] <- eb_fit
} 

save(eb_list_preds_doprot, file="./data/final_data/regression_outputs/eb_list_preds_doprot_w_srvy.RData")

# And the model with interactions
eb_complete$age_time <- eb_complete$age * eb_complete$surveyyear
eb_complete$sex_time <- as.numeric(eb_complete$sex) * eb_complete$surveyyear
eb_complete <- fastDummies::dummy_cols(eb_complete, select_columns = "isced_cat")
eb_complete$isced_basic_time <- eb_complete$isced_cat_Basic * eb_complete$surveyyear
eb_complete$isced_intermediate_time <- eb_complete$isced_cat_Intermediate * eb_complete$surveyyear
eb_complete$isced_advanced_time <- eb_complete$isced_cat_Advanced * eb_complete$surveyyear


interactions <- c("age_time", "sex_time", "isced_intermediate_time", "isced_advanced_time")

eb_list_interactions_doprot <- list()

 for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = "+ "))), sigma.formula = sigma.formula," + ", family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_interactions_doprot[[i]] <- eb_fit
} 

save(eb_list_interactions_doprot, file="./data/final_data/regression_outputs/eb_list_interactions_doprot_w_srvy.RData")
```

```{r}
# Questions about environment asked in 2 waves
eb_complete <- eb_tot %>% dplyr::select(surveyyear, envp_eg, effr_eg, sex, isced, urban, age, weightvec, isced_cat)
eb_complete <- eb_complete %>% drop_na()

# First empty model 
predictors <- c("surveyyear")
deps <- c("envp_eg", "effr_eg")

eb_list_empty_2011 <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_empty_2011[[i]] <- eb_fit
} 

summary(eb_list_empty_2011[[1]]) 

save(eb_list_empty_2011, file="./data/final_data/regression_outputs/eb_list_empty_2011_w_srvy.RData")

# Model with predictors
predictors <- c("surveyyear", "sex", "isced_cat", "age")
deps <- c("envp_eg", "effr_eg")

eb_list_preds_2011 <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_preds_2011[[i]] <- eb_fit
} 


save(eb_list_preds_2011, file="./data/final_data/regression_outputs/eb_list_preds_2011_w_new_srvy.RData")

# And the model with interactions
eb_complete$age_time <- eb_complete$age * eb_complete$surveyyear
eb_complete$sex_time <- as.numeric(eb_complete$sex) * eb_complete$surveyyear
eb_complete <- fastDummies::dummy_cols(eb_complete, select_columns = "isced_cat")
eb_complete$isced_basic_time <- eb_complete$isced_cat_Basic * eb_complete$surveyyear
eb_complete$isced_intermediate_time <- eb_complete$isced_cat_Intermediate * eb_complete$surveyyear
eb_complete$isced_advanced_time <- eb_complete$isced_cat_Advanced * eb_complete$surveyyear


interactions <- c("age_time", "sex_time", "isced_intermediate_time", "isced_advanced_time")

eb_list_interactions_2011 <- list()

 for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = "+ "))), sigma.formula = sigma.formula," + ", family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_interactions_2011[[i]] <- eb_fit
} 


save(eb_list_interactions_2011, file="./data/final_data/regression_outputs/eb_list_interactions_2011_w_srvy.RData")
```

```{r}
# Questions about naming climate change a problem
eb_complete <- eb_tot %>% dplyr::select(surveyyear, cchange2, cchangetot, sex, isced, urban, age, weightvec, isced_cat)
eb_complete <- eb_complete %>% drop_na()

# First empty model 
predictors <- c("surveyyear")
deps <- c("cchange2", "cchangetot")

eb_list_empty_cchange2 <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_empty_cchange2[[i]] <- eb_fit
} 

save(eb_list_empty_cchange2, file="./data/final_data/regression_outputs/eb_list_empty_cchange2_w_srvy.RData")

# Model with predictors
predictors <- c("surveyyear", "sex", "isced_cat", "age")
deps <- c("cchange2", "cchangetot")

eb_list_preds_cchange2 <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula,
                   family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_preds_cchange2[[i]] <- eb_fit
} 


save(eb_list_preds_cchange2, file="./data/final_data/regression_outputs/eb_list_preds_cchange2_w_srvy.RData")

# And the model with interactions
eb_complete$age_time <- eb_complete$age * eb_complete$surveyyear
eb_complete$sex_time <- as.numeric(eb_complete$sex) * eb_complete$surveyyear
eb_complete <- fastDummies::dummy_cols(eb_complete, select_columns = "isced_cat")
eb_complete$isced_basic_time <- eb_complete$isced_cat_Basic * eb_complete$surveyyear
eb_complete$isced_intermediate_time <- eb_complete$isced_cat_Intermediate * eb_complete$surveyyear
eb_complete$isced_advanced_time <- eb_complete$isced_cat_Advanced * eb_complete$surveyyear


interactions <- c("age_time", "sex_time", "isced_intermediate_time", "isced_advanced_time")

eb_list_interactions_cchange2 <- list()

 for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = "+ "))), sigma.formula = sigma.formula," + ", family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_interactions_cchange2[[i]] <- eb_fit
} 


save(eb_list_interactions_cchange2, file="./data/final_data/regression_outputs/eb_list_interactions_cchange2_w_srvy.RData")
```

```{r}
# Question about personal action taken
eb_complete <- eb_tot %>% dplyr::select(surveyyear, prsaction, sex, isced, urban, age, weightvec, isced_cat)
eb_complete <- eb_complete %>% drop_na()

# First empty model 
predictors <- c("surveyyear")
deps <- c("prsaction")

eb_list_empty_prsaction <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_empty_prsaction[[i]] <- eb_fit
} 


save(eb_list_empty_prsaction, file="./data/final_data/regression_outputs/eb_list_empty_prsaction_w_srvy.RData")

# Model with predictors
predictors <- c("surveyyear", "sex", "isced_cat", "age")
deps <- c("prsaction")

eb_list_preds_prsaction <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_preds_prsaction[[i]] <- eb_fit
} 

save(eb_list_preds_prsaction, file="./data/final_data/regression_outputs/eb_list_preds_prsaction_w_srvy.RData")

# And the model with interactions
eb_complete$age_time <- eb_complete$age * eb_complete$surveyyear
eb_complete$sex_time <- as.numeric(eb_complete$sex) * eb_complete$surveyyear
eb_complete <- fastDummies::dummy_cols(eb_complete, select_columns = "isced_cat")
eb_complete$isced_basic_time <- eb_complete$isced_cat_Basic * eb_complete$surveyyear
eb_complete$isced_intermediate_time <- eb_complete$isced_cat_Intermediate * eb_complete$surveyyear
eb_complete$isced_advanced_time <- eb_complete$isced_cat_Advanced * eb_complete$surveyyear

interactions <- c("age_time", "sex_time", "isced_intermediate_time", "isced_advanced_time")

eb_list_interactions_prsaction <- list()

 for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = "+ "))), sigma.formula = sigma.formula," + ", family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_interactions_prsaction[[i]] <- eb_fit
} 


save(eb_list_interactions_prsaction, file="./data/final_data/regression_outputs/eb_list_interactions_prsaction_w_srvy.RData")
```

```{r}
# Last item, whether the city undertakes enough action
eb_complete <- eb_tot %>% dplyr::select(surveyyear, doprot_city, sex, isced, urban, age, weightvec, isced_cat)
eb_complete <- eb_complete %>% drop_na()

# First empty model 
predictors <- c("surveyyear")
deps <- c("doprot_city")

eb_list_empty_doprot_city <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_empty_doprot_city[[i]] <- eb_fit
} 

save(eb_list_empty_doprot_city, file="./data/final_data/regression_outputs/eb_list_empty_doprot_city_w_srvy.RData")

# Model with predictors
predictors <- c("surveyyear", "sex", "isced_cat", "age")
deps <- c("doprot_city")

eb_list_preds_doprot_city <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_preds_doprot_city[[i]] <- eb_fit
} 


save(eb_list_preds_doprot_city, file="./data/final_data/regression_outputs/eb_list_preds_doprot_city_w_srvy.RData")

# And the model with interactions
eb_complete$age_time <- eb_complete$age * eb_complete$surveyyear
eb_complete$sex_time <- as.numeric(eb_complete$sex) * eb_complete$surveyyear
eb_complete <- fastDummies::dummy_cols(eb_complete, select_columns = "isced_cat")
eb_complete$isced_basic_time <- eb_complete$isced_cat_Basic * eb_complete$surveyyear
eb_complete$isced_intermediate_time <- eb_complete$isced_cat_Intermediate * eb_complete$surveyyear
eb_complete$isced_advanced_time <- eb_complete$isced_cat_Advanced * eb_complete$surveyyear


interactions <- c("age_time", "sex_time", "isced_intermediate_time", "isced_advanced_time")

eb_list_interactions_doprot_city <- list()

 for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = " + ")))
  # Perform the linear regression
  eb_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = "+ "))), sigma.formula = sigma.formula," + ", family=NO(mu.link = "identity", sigma.link = "identity"), data = eb_complete, weights = weightvec)
  
  eb_list_interactions_doprot_city[[i]] <- eb_fit
} 

save(eb_list_interactions_doprot_city, file="./data/final_data/regression_outputs/eb_list_interactions_doprot_city_w_srvy.RData")
```


## Motivaction {-}
```{r}
rm(list=ls())
load("./data/final_data/mottotal.RData")

# Gamlss cannot handle NAs, so I have to listwise delete all of them
mot_complete <- mottotal %>% drop_na()

# I want to build models. In the empty model, I only want to include time. 
predictors <- c("surveyyear")
deps <- c("cchange_mot", "worried_mot", "futuregen", "nowor", "ontime", "gov", "resp_gov", "resp_comp", "resp_mkb", "resp_citiz_mot", "resp_you", "pers_resp_mot", "sust_choice", "contr", "energy", "noidea", "motiv")

mot_list_empty <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression. The sigma formula pastes every variable one by one and calculates variance, the other formula shows the mean attitudes effects
  mot_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = mot_complete, weights = weightvec)
  
  mot_list_empty[[i]] <- mot_fit
} 

save(mot_list_empty, file="./data/final_data/regression_outputs/mot_list_empty_w_srvy.RData")

#Estimate a second model with the indicators + time
predictors <- c("surveyyear", "sex", "isced_cat", "age")
deps <- c("cchange_mot", "worried_mot", "futuregen", "nowor", "ontime", "gov", "resp_gov", "resp_comp", "resp_mkb", "resp_citiz_mot", "resp_you", "pers_resp_mot", "sust_choice", "contr", "energy", "noidea", "motiv")

mot_list_preds <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regrmotion
  mot_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = mot_complete, weights = weightvec)
  
  mot_list_preds[[i]] <- mot_fit
} 

save(mot_list_preds, file="./data/final_data/regression_outputs/mot_list_preds_w_srvy.RData")

#Now the last model with interaction of time on predictor variables
mot_complete$age_time <- mot_complete$age * mot_complete$surveyyear
mot_complete$sex_time <- as.numeric(mot_complete$sex) * mot_complete$surveyyear
mot_complete <- fastDummies::dummy_cols(mot_complete, select_columns = "isced_cat")
mot_complete$isced_basic_time <- mot_complete$isced_cat_Basic * mot_complete$surveyyear
mot_complete$isced_intermediate_time <- mot_complete$isced_cat_Intermediate * mot_complete$surveyyear
mot_complete$isced_advanced_time <- mot_complete$isced_cat_Advanced * mot_complete$surveyyear

interactions <- c("age_time", "sex_time", "isced_intermediate_time", "isced_advanced_time")


mot_list_interactions <- list()

 for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = " + ")))
  # Perform the linear regrmotion
  mot_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = "+ "))), sigma.formula = sigma.formula," + ", family=NO(mu.link = "identity", sigma.link = "identity"), data = mot_complete, weights = weightvec)
  
  mot_list_interactions[[i]] <- mot_fit
} 


save(mot_list_interactions, file="./data/final_data/regression_outputs/mot_list_interactions_w_srvy.RData")

```

## LISS {-}
```{r}
rm(list=ls())
load("./data/final_data/lisstotal.RData")

# Gamlss cannot handle NAs, so I have to listwise delete all of them
liss_complete <- lisstotal %>% drop_na()

# I want to build models. In the empty model, I only want to include time. 
predictors <- c("surveyyear")
deps <- c("lifestyle")

liss_list_empty <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression. The sigma formula pastes every variable one by one and calculates variance, the other formula shows the mean attitudes effects
  liss_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = liss_complete, weights = weightvec)
  
  liss_list_empty[[i]] <- liss_fit
} 


save(liss_list_empty, file="./data/final_data/regression_outputs/liss_list_empty_w_srvy.RData")

#Estimate a second model with the indicators + time
predictors <- c("surveyyear", "sex", "isced_cat", "age")
deps <- c("lifestyle")


liss_list_preds <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regrlission
  liss_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = liss_complete, weights = weightvec)
  
  liss_list_preds[[i]] <- liss_fit
} 


save(liss_list_preds, file="./data/final_data/regression_outputs/liss_list_preds_w_srvy.RData")



#Now the last model with interaction of time on predictor variables
liss_complete$age_time <- liss_complete$age * liss_complete$surveyyear
liss_complete$sex_time <- as.numeric(liss_complete$sex) * liss_complete$surveyyear
liss_complete <- fastDummies::dummy_cols(liss_complete, select_columns = "isced_cat")
liss_complete$isced_basic_time <- liss_complete$isced_cat_Basic * liss_complete$surveyyear
liss_complete$isced_intermediate_time <- liss_complete$isced_cat_Intermediate * liss_complete$surveyyear
liss_complete$isced_advanced_time <- liss_complete$isced_cat_Advanced * liss_complete$surveyyear

interactions <- c("age_time", "sex_time", "isced_intermediate_time", "isced_advanced_time")

liss_list_interactions <- list()

 for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = " + ")))
  # Perform the linear regression
  liss_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = "+ "))), sigma.formula = sigma.formula," + ", family=NO(mu.link = "identity", sigma.link = "identity"), data = liss_complete, weights = weightvec)
  
  liss_list_interactions[[i]] <- liss_fit
} 


save(liss_list_interactions, file="./data/final_data/regression_outputs/liss_list_interactions_w_srvy.RData")
```

## SOCON {-}
```{r}
rm(list=ls())
load("./data/final_data/socontotal.RData")

# Gamlss cannot handle NAs, so I have to listwise delete all of them
socon_complete <- socontotal %>% drop_na()

# I want to build models. In the empty model, I only want to include time. 
predictors <- c("surveyyear")
deps <- c("fut_gen_socon")


socon_list_empty <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression. The sigma formula pastes every variable one by one and calculates variance, the other formula shows the mean attitudes effects
  socon_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = socon_complete, weights = weightvec)
  
  socon_list_empty[[i]] <- socon_fit
} 

save(socon_list_empty, file="./data/final_data/regression_outputs/socon_list_empty_w_srvy.RData")

#Estimate a second model with the indicators + time
predictors <- c("surveyyear", "sex", "isced_cat", "age")
deps <- c("fut_gen_socon")


socon_list_preds <- list()

# Loop through each dependent variable
  for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + ")))
  # Perform the linear regression
  socon_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "))), sigma.formula = sigma.formula, family=NO(mu.link = "identity", sigma.link = "identity"), data = socon_complete, weights = weightvec)
  
  socon_list_preds[[i]] <- socon_fit
} 

summary(socon_list_preds[[1]]) 

save(socon_list_preds, file="./data/final_data/regression_outputs/socon_list_preds_w_srvy.RData")

#Now the last model with interaction of time on predictor variables
socon_complete$age_time <- socon_complete$age * socon_complete$surveyyear
socon_complete$sex_time <- as.numeric(socon_complete$sex) * socon_complete$surveyyear
socon_complete <- fastDummies::dummy_cols(socon_complete, select_columns = "isced_cat")
socon_complete$isced_basic_time <- socon_complete$isced_cat_Basic * socon_complete$surveyyear
socon_complete$isced_intermediate_time <- socon_complete$isced_cat_Intermediate * socon_complete$surveyyear
socon_complete$isced_advanced_time <- socon_complete$isced_cat_Advanced * socon_complete$surveyyear

interactions <- c("age_time", "sex_time", "isced_intermediate_time", "isced_advanced_time")


socon_list_interactions <- list()

 for (i in 1:length(deps)) {
  # Specify the sigma formula
  sigma.formula <- as.formula(paste("~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = " + ")))
  # Perform the linear regression
  socon_fit <- gamlss(as.formula(paste(deps[i], "~", paste(predictors, collapse = " + "), " + ", paste(interactions, collapse = "+ "))), sigma.formula = sigma.formula," + ", family=NO(mu.link = "identity", sigma.link = "identity"), data = socon_complete, weights = weightvec)
  
  socon_list_interactions[[i]] <- socon_fit
} 


save(socon_list_interactions, file="./data/final_data/regression_outputs/socon_list_interactions_w_srvy.RData")

```


