---
title: "Untitled"
author: "Anuschka Peelen"
date: "`r Sys.Date()`"
output: html_document
---


```{r}
rm(list=ls())
library(meta)
library(metafor)
library(here)
here()
```

```{r}
# Try to repeat this with my "own" data

results_reg_tot <- rbind(results_reg_dpes, results_reg_ess)


intercept_reg <- metareg(results_reg_tot$intercept, ~ results_reg_tot$year) #Doesnt work yet because I have to define the model first, which I do with the following code: 

intercept.gen <- metagen(TE = intercept,
                 seTE = std_dev,
                 data = results_reg_tot,
                 intercept = "M",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE)

summary(intercept.gen)

intercept_reg <- metareg(intercept.gen, ~results_reg_tot$surveyyear + results_reg_tot$data_coll_procedure)
# It throws out redundant variables, and apparently data collection procedure was such a redundant variable
intercept_reg <- metareg(intercept.gen, ~results_reg_tot$surveyyear + results_reg_tot$meas_education)
intercept_reg <- metareg(intercept.gen, ~results_reg_tot$surveyyear + results_reg_tot$meas_lr)
intercept_reg <- metareg(intercept.gen, ~results_reg_tot$surveyyear + results_reg_tot$meas_religion)

# Of course, nothing is sig yet

summary(intercept_reg)

forest(intercept_reg)

#Repeat the same for the variance (and thus polarization)

variance.gen <- metagen(TE = variance,
                 seTE = std_dev,
                 data = results_reg_tot,
                 intercept = "var",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE)

variance_reg <- metareg(variance.gen, ~results_reg_tot$surveyyear + results_reg_tot$data_coll_procedure)
summary(variance_reg)
variance_reg <- metareg(variance.gen, ~results_reg_tot$surveyyear + results_reg_tot$meas_education)
variance_reg <- metareg(variance.gen, ~results_reg_tot$surveyyear + results_reg_tot$meas_lr)
variance_reg <- metareg(variance.gen, ~results_reg_tot$surveyyear + results_reg_tot$meas_religion)


```


```{r}
# With the final data
# This method is not for multiple regression
load(here("./climatechange/data/meta_analysis", "total_reg_results.RData"))

?metagen

time_intercept_gen <- metagen(TE = mu_time,
                 seTE = mu_time_sd,
                 data = total_reg_results,
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE)

k <- summary(time_intercept_gen$random[8])
time_effect_empty_reg <- metareg(time_intercept_gen, ~ total_reg_results$first_year)


summary(time_effect_empty_reg)

# The overall effect is stored in the 
g <- time_intercept_gen$random

# This effect is not significant. What about the variance?

time.variance.gen <- metagen(TE = sig_time,
                 seTE = sig_time_sd,
                 data = total_reg_results,
                 intercept = "M",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE)

summary(time.variance.gen)
time_variance_empty_reg <- metareg(time.variance.gen, ~ total_reg_results$first_year)
summary(time_variance_empty_reg)

#Also not significant

# How about the effects with predictor variables
time_preds_gen <- metagen(TE = mu_time_pred,
                 seTE = mu_time_sd_pred,
                 data = total_reg_results,
                 intercept = "M",
                 fixed = FALSE,
                 random = TRUE,
                 method.tau = "REML",
                 hakn = TRUE)

summary(time_preds_gen)
time_effect_preds_reg <- metareg(time_preds_gen, ~ total_reg_results$first_year)
summary(time_effect_preds_reg)


```

```{r}
# Step 1. Estimate the empty model without moderators to make the forest plots. 
model_step_1_att <- rma(yi = mu_time,
              sei = mu_time_sd,
              data = total_reg_results,
              method = "ML",
              test = "knha")

model_step_1_att

# I want to assign different colors to the different types of dependent variables, so that one can easily distinguish 
# the types of attitudes by colors in the forest plot
total_reg_results$colour <- NA
total_reg_results$colour[total_reg_results$attitude_cat=="cognitive"] <- "#2980B9" # blue
total_reg_results$colour[total_reg_results$attitude_cat=="affective"] <- "#CC5279" # pink
total_reg_results$colour[total_reg_results$attitude_cat=="behavioral"] <- "#B0CC52" # green

colour.palette <- as.vector(total_reg_results$colour)

# Make a forest plot (has to be done outside codechunk, otherwise it doesn't save)
```

# Time effect 
png(file = "/Users/anuschka/Documents/forestplot.png", width = 2800, height = 2400, res = 300)

png <- forest(model_step_1_att, colout = colour.palette, col = "#ACBFD6", annotate = TRUE, header = "Forest plot time effect attitudes", slab = total_reg_results$dep_var, pch = 23,fonts = "Helvetica", cex = 0.5, mlab = "Pooled estimate", ilab = attitudes, ilab.xpos = -2, xlim = c(-1, 1))

dev.off()

```{r}
# Repeat step 1, but then for the polarization (variance)
model_step_1_var <- rma(yi = sig_time,
              sei = sig_time_sd,
              data = total_reg_results,
              method = "ML", #waarom ml niet reml?
              test = "knha")

model_step_1_var

# And also make the forest plot for the variance
```

# Time variance plot
png(file = "/Users/anuschka/Documents/forestplot_var.png", width = 2800, height = 2400, res = 300)

png <- forest(model_step_1_var, colout = colour.palette, col = "#ACBFD6", annotate = TRUE, header = "Forest plot time effect attitudes", slab = total_reg_results$dep_var, pch = 23,fonts = "Helvetica", cex = 0.5, mlab = "Pooled estimate", ilab = attitudes, ilab.xpos = -2, xlim = c(-1, 1))

dev.off()

```{r}
#Using the kable package to make a nice table
library(kableExtra)





```

```{r}
#Step 2. Empty model with meta-level indicators
model_step_2_att <- rma(yi = mu_time,
              sei = mu_time_sd,
              data = total_reg_results,
              mods = ~ first_year + attitude_cat,
              method = "ML",
              test = "knha")

model_step_2_att


```
```{r}
# Step 2 variance
#Step 2. Empty model with meta-level indicators
model_step_2_var <- rma(yi = sig_time,
              sei = sig_time_sd,
              data = total_reg_results,
              mods = ~ first_year + attitude_cat,
              method = "ML",
              test = "knha")

model_step_2_var
```

```{r}
# Step 3. Model with independent variables
model_step_3_att <- rma(yi = mu_time_pred,
              sei = mu_time_sd_pred,
              data = total_reg_results,
              mods = ~ first_year + attitude_cat,
              method = "ML",
              test = "knha")

model_step_3_att
```

```{r}
# Step 3. Variance
model_step_3_var <- rma(yi = sig_time_pred,
              sei = sig_time_sd_pred,
              data = total_reg_results,
              mods = ~ first_year + attitude_cat,
              method = "ML",
              test = "knha")

model_step_3_var
```

```{r}
# Step 4. Model with interactions
model_step_4_att <- rma(yi = mu_time_int,
              sei = mu_time_sd_int,
              data = total_reg_results,
              mods = ~ first_year + attitude_cat,
              method = "ML",
              test = "knha")

model_step_4_att

```
```{r}
# Step 4. Variance
model_step_4_var <- rma(yi = sig_time_int,
              sei = sig_time_sd_int,
              data = total_reg_results,
              mods = ~ first_year + attitude_cat,
              method = "ML",
              test = "knha")

model_step_4_var
```





```{r}
# Practice with kable package
library(tidyverse)
library(kableExtra)
install.packages("modelsummary")
library(modelsummary)
library(broom)
install.packages("apaTables")
library(apaTables)

dt <- mtcars[1:5, 1:6]
kbl(dt)

dt %>%
  kbl(caption = "Table 1. Regression outputs") %>%
  kable_classic(full_width = F, html_font = "Times")


model <- as.data.frame(summary(model_step_1_att))
model <- tidy(model)

model <- tidy(summary(model_step_1_att))






model %>% 
  kbl(caption = "Table 1. Regression outputs") %>% 
  kable_classic(full_width = F, html_font = "Times")


regression_table <- data.frame(model = NA, I2 = NA)
regression_table$model <- "Step 1 var"

regression_table$I2 <- model_step_1_att$I2
regression_table$intercept <- coef(model_step_1_att)["(Intercept"]



```

