---
title: "Untitled"
author: "Anuschka Peelen"
date: "`r Sys.Date()`"
output: html_document
---
# weighed gamlss - waves 

```{r}
rm(list=ls())
library(meta)
library(metafor)
library(dplyr)
library(here)
here()
here::i_am("scripts/analysis/meta_analysis_gamlss_weigh.Rmd")
```

```{r}
# With the final data
# This method is not for multiple regression
load(here("./data/meta_analysis", "total_results_waves.RData"))
load(here("./data/meta_analysis", "total_reg_results_gam_w.RData"))
load("/Users/anuschka/Documents/climatechange/climatechange/data/meta_analysis/total_results_waves.RData")

mean_year <- select(total_reg_results, dep_var, mean_year)

total_results_waves <- left_join(total_results_waves, mean_year)
total_results_waves <- total_results_waves[-(53:58), ] 
```

```{r}
# Step 1. Estimate the empty model without moderators to make the forest plots. 
model_step_1_att <- rma(yi = mu_time,
              sei = mu_time_sd,
              data = total_results_waves,
              method = "ML",
              test = "knha")

model_step_1_att

# I want to assign different colors to the different types of dependent variables, so that one can easily distinguish 
# the types of attitudes by colors in the forest plot
total_results_waves$colour <- NA
total_results_waves$colour[total_results_waves$attitude_cat=="cognitive"] <- "#2980B9" # blue
total_results_waves$colour[total_results_waves$attitude_cat=="affective"] <- "#CC5279" # pink
total_results_waves$colour[total_results_waves$attitude_cat=="behavioral"] <- "#B0CC52" # green

colour.palette <- as.vector(total_results_waves$colour)

# Make a forest plot (has to be done outside codechunk, otherwise it doesn't save)
# The argument order = "yi" puts the effects in order from negative to positive
png <- forest(model_step_1_att, colout = colour.palette, col = "#ACBFD6", annotate = TRUE, header = "Forest plot time effect attitudes", slab = total_reg_results$dep_var, pch = 23,fonts = "Helvetica", cex = 0.5, mlab = "Pooled estimate", ilab = attitude_cat, ilab.xpos = -2, xlim = c(-1, 1), order = "yi")

# And this is how you order it per year
png <- forest(model_step_1_att, colout = colour.palette, col = "#ACBFD6", annotate = TRUE, header = "Forest plot time effect attitudes", slab = total_reg_results$dep_var, pch = 23,fonts = "Helvetica", cex = 0.5, mlab = "Pooled estimate", ilab = attitude_cat, ilab.xpos = -2, xlim = c(-1, 1), order = total_reg_results$mean_year)

```

# Time effect 
png(file = "/Users/anuschka/Documents/climatechange/climatechange/output/forestplot_neg_to_pos_weight_waves.png", width = 2800, height = 2400, res = 300)

png <- forest(model_step_1_att, colout = colour.palette, col = "#ACBFD6", annotate = TRUE, header = "Forest plot time effect attitudes", slab = total_results_waves$dep_var_wave, pch = 23,fonts = "Helvetica", cex = 0.5, mlab = "Pooled estimate", ilab.xpos = -2, xlim = c(-1, 1), order = "yi")

dev.off()

```{r}
# Repeat step 1, but then for the polarization (variance)
model_step_1_var <- rma(yi = sig_time,
              sei = sig_time_sd,
              data = total_results_waves,
              method = "ML", #waarom ml niet reml?
              test = "knha")

model_step_1_var

# And also make the forest plot for the variance
```

# Time variance plot
png(file = "/Users/anuschka/Documents/climatechange/climatechange/output/forestplot_neg_to_pos_weight_waves_var.png", width = 2800, height = 2400, res = 300)

png <- forest(model_step_1_var, colout = colour.palette, col = "#ACBFD6", annotate = TRUE, header = "Forest plot time effect attitudes", slab = total_results_waves$dep_var_wave, pch = 23,fonts = "Helvetica", cex = 0.5, mlab = "Pooled estimate", ilab = attitude_cat, ilab.xpos = -2, xlim = c(-1, 1), order = "yi")

dev.off()

```{r}
#Step 2. Empty model with meta-level indicators
model_step_2_att <- rma(yi = mu_time,
              sei = mu_time_sd,
              data = total_results_waves,
              mods = ~ mean_year + attitude_cat + ambiguous,
              method = "ML",
              test = "knha")

model_step_2_att


```
```{r}
# Step 2 variance
#Step 2. Empty model with meta-level indicators
model_step_2_var <- rma(yi = sig_time,
              sei = sig_time_sd,
              data = total_results_waves,
              mods = ~ mean_year + attitude_cat + ambiguous,
              method = "ML",
              test = "knha")

model_step_2_var

```

```{r}
# Step 3. Model with independent variables
model_step_3_att <- rma(yi = mu_time_pred,
              sei = mu_time_sd_pred,
              data = total_results_waves,
              mods = ~ mean_year + attitude_cat + ambiguous,
              method = "ML",
              test = "knha")

model_step_3_att
```

```{r}
# Step 3. Variance
model_step_3_var <- rma(yi = sig_time_pred,
              sei = sig_time_sd_pred,
              data = total_results_waves,
              mods = ~ mean_year + attitude_cat + ambiguous,
              method = "ML",
              test = "knha")

model_step_3_var
```

```{r}
# Step 4. Model with interactions
model_step_4_att <- rma(yi = mu_time_int,
              sei = mu_time_sd_int,
              data = total_results_waves,
              mods = ~ mean_year + attitude_cat + ambiguous,
              method = "ML",
              test = "knha")

model_step_4_att

```
```{r}
# Step 4. Variance
model_step_4_var <- rma(yi = sig_time_int,
              sei = sig_time_sd_int,
              data = total_results_waves,
              mods = ~ mean_year + attitude_cat + ambiguous,
              method = "ML",
              test = "knha")

model_step_4_var
```


```{r}
# Estimate the model while controlling for ambiguity of variables
model_test_att <- rma(yi = mu_time,
              sei = mu_time_sd,
              data = total_reg_results,
              mods = ~ first_year + attitude_cat + ambiguous,
              method = "ML",
              test = "knha")

model_test_att

# And run the model on a subset of the data without the ambiguous results
total_reg_sub <- subset(total_reg_results, ambiguous == "No")
# These are then 37 variables
model_test_sub <- rma(yi = mu_time,
              sei = mu_time_sd,
              data = total_reg_sub,
              mods = ~ first_year + attitude_cat,
              method = "ML",
              test = "knha")

model_test_sub

# See if there is an effect without the inclusion of meta-level variables
model <- rma(yi = mu_time,
              sei = mu_time_sd,
              data = total_reg_sub,
              method = "ML",
              test = "knha")

model
# Still not significant, so that seems rather robust
```



```{r}
# Practice with kable package
library(tidyverse)
library(kableExtra)
install.packages("modelsummary")
library(modelsummary)
library(broom)
install.packages("apaTables")
library(apaTables)

dt <- mtcars[1:5, 1:6]
kbl(dt)

dt %>%
  kbl(caption = "Table 1. Regression outputs") %>%
  kable_classic(full_width = F, html_font = "Times")


model <- as.data.frame(summary(model_step_1_att))
model <- tidy(model)

model <- tidy(summary(model_step_1_att))






model %>% 
  kbl(caption = "Table 1. Regression outputs") %>% 
  kable_classic(full_width = F, html_font = "Times")


regression_table <- data.frame(model = NA, I2 = NA)
regression_table$model <- "Step 1 var"

regression_table$I2 <- model_step_1_att$I2
regression_table$intercept <- coef(model_step_1_att)["(Intercept"]



```

