---
title: "Untitled"
author: "Anuschka Peelen"
date: "`r Sys.Date()`"
output: html_document
---
# weighed gamlss - waves 

```{r}
rm(list=ls())
library(meta)
library(metafor)
library(dplyr)
library(here)
library(kableExtra)
here()
here::i_am("scripts/analysis/meta_analysis_gw_waves.Rmd")
```

```{r}
# With the final data
load(here("./data/meta_analysis", "total_results_waves_new.RData"))
```

```{r}
# Step 1. Estimate the empty model without moderators to make the forest plots. 
model_step_1_att <- rma(yi = mu_time,
              sei = mu_time_sd,
              data = total_results_waves,
              method = "ML",
              test = "knha")

model_step_1_att

# I want to assign different colors to the different types of dependent variables, so that one can easily distinguish 
# the types of attitudes by colors in the forest plot
total_results_waves$colour <- NA
total_results_waves$colour[total_results_waves$attitude_cat=="cognitive"] <- "#2980B9" # blue
total_results_waves$colour[total_results_waves$attitude_cat=="affective"] <- "#CC5279" # pink
total_results_waves$colour[total_results_waves$attitude_cat=="behavioral"] <- "#B0CC52" # green

colour.palette <- as.vector(total_results_waves$colour)

# Make a forest plot (has to be done outside codechunk, otherwise it doesn't save)
# The argument order = "yi" puts the effects in order from negative to positive
png <- forest(model_step_1_att, colout = colour.palette, col = "#ACBFD6", annotate = TRUE, header = "Forest plot time effect attitudes", slab = total_reg_results$dep_var, pch = 23,fonts = "Helvetica", cex = 0.5, mlab = "Pooled estimate", ilab = attitude_cat, ilab.xpos = -2, xlim = c(-1, 1), order = "yi")

# And this is how you order it per year
png <- forest(model_step_1_att, colout = colour.palette, col = "#ACBFD6", annotate = TRUE, header = "Forest plot time effect attitudes", slab = total_reg_results$dep_var, pch = 23,fonts = "Helvetica", cex = 0.5, mlab = "Pooled estimate", ilab = attitude_cat, ilab.xpos = -2, xlim = c(-1, 1), order = total_reg_results$mean_year)

```

# Time effect 
png(file = "/Users/anuschka/Documents/climatechange/climatechange/output/forestplot_neg_to_pos_weight_waves.png", width = 2800, height = 2400, res = 300)

png <- forest(model_step_1_att, colout = colour.palette, col = "#ACBFD6", annotate = TRUE, header = "Forest plot time effect attitudes", slab = total_results_waves$dep_var_wave, pch = 23,fonts = "Helvetica", cex = 0.5, mlab = "Pooled estimate", ilab.xpos = -2, xlim = c(-1, 1), order = "yi")

dev.off()

```{r}
# Repeat step 1, but then for the polarization (variance)
model_step_1_var <- rma(yi = sig_time,
              sei = sig_time_sd,
              data = total_results_waves,
              method = "ML", #waarom ml niet reml?
              test = "knha")

model_step_1_var

# And also make the forest plot for the variance
```

# Time variance plot
png(file = "/Users/anuschka/Documents/climatechange/climatechange/output/forestplot_neg_to_pos_weight_waves_var.png", width = 2800, height = 2400, res = 300)

png <- forest(model_step_1_var, colout = colour.palette, col = "#ACBFD6", annotate = TRUE, header = "Forest plot time effect attitudes", slab = total_results_waves$dep_var_wave, pch = 23,fonts = "Helvetica", cex = 0.5, mlab = "Pooled estimate", ilab = attitude_cat, ilab.xpos = -2, xlim = c(-1, 1), order = "yi")

dev.off()

```{r}
#Step 2. Empty model with meta-level indicators
model_step_2_att <- rma(yi = mu_time,
              sei = mu_time_sd,
              data = total_results_waves,
              mods = ~ mean_year + attitude_cat + ambiguous + fin_crisis + covid,
              method = "ML",
              test = "knha")

model_step_2_att


```
```{r}
# Step 2 variance
#Step 2. Empty model with meta-level indicators
model_step_2_var <- rma(yi = sig_time,
              sei = sig_time_sd,
              data = total_results_waves,
              mods = ~ mean_year + attitude_cat + ambiguous + fin_crisis + covid,
              method = "ML",
              test = "knha")

model_step_2_var

```

```{r}
# Step 3. Model with independent variables
model_step_3_att <- rma(yi = mu_time_pred,
              sei = mu_time_sd_pred,
              data = total_results_waves,
              mods = ~ mean_year + attitude_cat + ambiguous + fin_crisis + covid,
              method = "ML",
              test = "knha")

model_step_3_att
```

```{r}
# Step 3. Variance
model_step_3_var <- rma(yi = sig_time_pred,
              sei = sig_time_sd_pred,
              data = total_results_waves,
              mods = ~ mean_year + attitude_cat + ambiguous + fin_crisis + covid,
              method = "ML",
              test = "knha")

model_step_3_var
```

```{r}
# Step 4. Model with interactions
model_step_4_att <- rma(yi = mu_time_int,
              sei = mu_time_sd_int,
              data = total_results_waves,
              mods = ~ mean_year + attitude_cat + ambiguous + fin_crisis + covid,
              method = "ML",
              test = "knha")

model_step_4_att

```
```{r}
# Step 4. Variance
model_step_4_var <- rma(yi = sig_time_int,
              sei = sig_time_sd_int,
              data = total_results_waves,
              mods = ~ mean_year + attitude_cat + ambiguous + fin_crisis + covid,
              method = "ML",
              test = "knha")

model_step_4_var
```

```{r}
options(knitr.kable.NA = '')
```



```{r}

# Make a kable table of all the models 
# First the mean attitudes, that i want in the table next to each other
# Time effect only model
model_1_mean_df <- data.frame(matrix(ncol = 5, nrow = 7))
colnames(model_1_mean_df) <- c("Mu/Sigma", "Variable", "Estimate", "SE", "p")
model_1_mean_df$Variable <- c("Intercept", "Mean year", "Attitude behavioral (ref = aff)", "Attitude cognitive", "Ambigious (ref = no)", "Financial crisis", "Covid-19")
model_1_mean_df$`Mu/Sigma` <- c("Mu", "", "", "", "", "", "")

model_1_mean_df$Estimate <- as.numeric(model_step_2_att$beta) #estimate
model_1_mean_df$SE <- model_step_2_att$se #se indeed but as a row
model_1_mean_df$p <- model_step_2_att$pval # same as for SE


model_1_mean_df$p_text <- case_when(
model_1_mean_df$p >= 0.05 ~ "",
model_1_mean_df$p < 0.001 ~ "***",
model_1_mean_df$p < 0.01 ~ "**",
model_1_mean_df$p < 0.05 ~ "*"
)

# I also want the R2, I2 and QE in the table
model_1_fit  <- data.frame(matrix(ncol = 6, nrow = 3))
colnames(model_1_fit) <- c("Mu/Sigma", "Variable", "Estimate", "SE", "p", "p_text")
model_1_fit$Variable <- c("R2", "I2", "QE")
model_1_fit$Estimate <- c(model_step_2_att$R2, model_step_2_att$I2, model_step_2_att$QE)

model_1_mean_df <- rbind(model_1_mean_df, model_1_fit)


# Independent variable model 
model_2_mean_df <- data.frame(matrix(ncol = 5, nrow = 7))
colnames(model_2_mean_df) <- c("Mu/Sigma", "Variable", "Estimate", "SE", "p")
model_2_mean_df$Variable <- c("Intercept", "Mean year", "Attitude behavioral (ref = aff)", "Attitude cognitive", "Ambigious (ref = no)", "Financial crisis", "Covid-19")
model_2_mean_df$`Mu/Sigma` <- c("Mu", "", "", "", "", "", "")

model_2_mean_df$Estimate <- as.numeric(model_step_3_att$beta) #estimate
model_2_mean_df$SE <- model_step_3_att$se #se indeed but as a row
model_2_mean_df$p <- model_step_3_att$pval # same as for SE


model_2_mean_df$p_text <- case_when(
model_2_mean_df$p >= 0.05 ~ "",
model_2_mean_df$p < 0.001 ~ "***",
model_2_mean_df$p < 0.01 ~ "**",
model_2_mean_df$p < 0.05 ~ "*"
)

# I also want the R2, I2 and QE in the table
model_2_fit  <- data.frame(matrix(ncol = 6, nrow = 3))
colnames(model_2_fit) <- c("Mu/Sigma", "Variable", "Estimate", "SE", "p", "p_text")
model_2_fit$Variable <- c("R2", "I2", "QE")
model_2_fit$Estimate <- c(model_step_3_att$R2, model_step_3_att$I2, model_step_3_att$QE)

model_2_mean_df <- rbind(model_2_mean_df, model_2_fit)


#And the interaction model
model_3_mean_df <- data.frame(matrix(ncol = 5, nrow = 7))
colnames(model_3_mean_df) <- c("Mu/Sigma", "Variable", "Estimate", "SE", "p")
model_3_mean_df$Variable <- c("Intercept", "Mean year", "Attitude behavioral (ref = aff)", "Attitude cognitive", "Ambigious (ref = no)", "Financial crisis", "Covid-19")
model_3_mean_df$`Mu/Sigma` <- c("Mu", "", "", "", "", "", "")

model_3_mean_df$Estimate <- as.numeric(model_step_4_att$beta) #estimate
model_3_mean_df$SE <- model_step_4_att$se #se indeed but as a row
model_3_mean_df$p <- model_step_4_att$pval # same as for SE


model_3_mean_df$p_text <- case_when(
model_3_mean_df$p >= 0.05 ~ "",
model_3_mean_df$p < 0.001 ~ "***",
model_3_mean_df$p < 0.01 ~ "**",
model_3_mean_df$p < 0.05 ~ "*"
)

# I also want the R2, I2 and QE in the table
model_3_fit  <- data.frame(matrix(ncol = 6, nrow = 3))
colnames(model_3_fit) <- c("Mu/Sigma", "Variable", "Estimate", "SE", "p", "p_text")
model_3_fit$Variable <- c("R2", "I2", "QE")
model_3_fit$Estimate <- c(model_step_4_att$R2, model_step_4_att$I2, model_step_4_att$QE)

model_3_mean_df <- rbind(model_3_mean_df, model_3_fit)

total_mean <- cbind(model_1_mean_df, model_2_mean_df, model_3_mean_df)

# Now for the sigma
model_1_var_df <- data.frame(matrix(ncol = 5, nrow = 7))
colnames(model_1_var_df) <- c("Mu/Sigma", "Variable", "Estimate", "SE", "p")
model_1_var_df$Variable <- c("Intercept", "Var year", "Varitude behavioral (ref = aff)", "Varitude cognitive", "Ambigious (ref = no)", "Financial crisis", "Covid-19")
model_1_var_df$`Mu/Sigma` <- c("Sigma", "", "", "", "", "", "")

model_1_var_df$Estimate <- as.numeric(model_step_2_var$beta) #estimate
model_1_var_df$SE <- model_step_2_var$se #se indeed but as a row
model_1_var_df$p <- model_step_2_var$pval # same as for SE


model_1_var_df$p_text <- case_when(
model_1_var_df$p >= 0.05 ~ "",
model_1_var_df$p < 0.001 ~ "***",
model_1_var_df$p < 0.01 ~ "**",
model_1_var_df$p < 0.05 ~ "*"
)

# I also want the R2, I2 and QE in the table
model_1_fit  <- data.frame(matrix(ncol = 6, nrow = 3))
colnames(model_1_fit) <- c("Mu/Sigma", "Variable", "Estimate", "SE", "p", "p_text")
model_1_fit$Variable <- c("R2", "I2", "QE")
model_1_fit$Estimate <- c(model_step_2_var$R2, model_step_2_var$I2, model_step_2_var$QE)

model_1_var_df <- rbind(model_1_var_df, model_1_fit)


# Independent variable model 
model_2_var_df <- data.frame(matrix(ncol = 5, nrow = 7))
colnames(model_2_var_df) <- c("Mu/Sigma", "Variable", "Estimate", "SE", "p")
model_2_var_df$Variable <- c("Intercept", "Var year", "Varitude behavioral (ref = aff)", "Varitude cognitive", "Ambigious (ref = no)", "Financial crisis", "Covid-19")
model_2_var_df$`Mu/Sigma` <- c("Sigma", "", "", "", "", "", "")

model_2_var_df$Estimate <- as.numeric(model_step_3_var$beta) #estimate
model_2_var_df$SE <- model_step_3_var$se #se indeed but as a row
model_2_var_df$p <- model_step_3_var$pval # same as for SE


model_2_var_df$p_text <- case_when(
model_2_var_df$p >= 0.05 ~ "",
model_2_var_df$p < 0.001 ~ "***",
model_2_var_df$p < 0.01 ~ "**",
model_2_var_df$p < 0.05 ~ "*"
)

# I also want the R2, I2 and QE in the table
model_2_fit  <- data.frame(matrix(ncol = 6, nrow = 3))
colnames(model_2_fit) <- c("Mu/Sigma", "Variable", "Estimate", "SE", "p", "p_text")
model_2_fit$Variable <- c("R2", "I2", "QE")
model_2_fit$Estimate <- c(model_step_3_var$R2, model_step_3_var$I2, model_step_3_var$QE)

model_2_var_df <- rbind(model_2_var_df, model_2_fit)


#And the interaction model
model_3_var_df <- data.frame(matrix(ncol = 5, nrow = 7))
colnames(model_3_var_df) <- c("Mu/Sigma", "Variable", "Estimate", "SE", "p")
model_3_var_df$Variable <- c("Intercept", "Var year", "Varitude behavioral (ref = aff)", "Varitude cognitive", "Ambigious (ref = no)", "Financial crisis", "Covid-19")
model_3_var_df$`Mu/Sigma` <- c("Sigma", "", "", "", "", "", "")

model_3_var_df$Estimate <- as.numeric(model_step_4_var$beta) #estimate
model_3_var_df$SE <- model_step_4_var$se #se indeed but as a row
model_3_var_df$p <- model_step_4_var$pval # same as for SE

model_3_var_df$p_text <- case_when(
model_3_var_df$p >= 0.05 ~ "",
model_3_var_df$p < 0.001 ~ "***",
model_3_var_df$p < 0.01 ~ "**",
model_3_var_df$p < 0.05 ~ "*"
)

# I also want the R2, I2 and QE in the table
model_3_fit  <- data.frame(matrix(ncol = 6, nrow = 3))
colnames(model_3_fit) <- c("Mu/Sigma", "Variable", "Estimate", "SE", "p", "p_text")
model_3_fit$Variable <- c("R2", "I2", "QE")
model_3_fit$Estimate <- c(model_step_4_var$R2, model_step_4_var$I2, model_step_4_var$QE)

model_3_var_df <- rbind(model_3_var_df, model_3_fit)

total_var <- cbind(model_1_var_df, model_2_var_df, model_3_var_df)

#Now a total dataframe with both models together, and then make some changes before making the table
total_meta <- rbind(total_mean, total_var)
colnames(total_meta) <- c("mu_sigma", "variable_empty", "est_empty", "se_empty", "p_empty", "p_text_empty", "mu_sigma_indep", "variable_indep", "est_indep", "se_indep", "p_indep", "p_text_indep", "mu_sigma_inter", "variable_inter", "est_inter", "se_inter", "p_inter", "p_text_inter" )
rownames(total_meta) <- NULL
total_meta <- dplyr::select(total_meta, mu_sigma, variable_empty, est_empty, se_empty, p_text_empty, est_indep, se_indep, p_text_indep, est_inter, se_inter, p_text_inter)

total_meta <- mutate_at(total_meta, vars(est_empty, se_empty, est_indep, se_indep, est_inter, se_inter), as.numeric)
numeric_cols <- sapply(total_meta, is.numeric)
total_meta[, numeric_cols] <- round(total_meta[, numeric_cols], digits = 3)

kable(total_meta, digits = 3, caption = "Appendix X. Meta-regression on climate change attitudes and polarization per wave", 
      col.names = c( "", "Variables", "Estimate", "Std. Error", "", "Estimate", "Std. Error", "", "Estimate", "Std. Error", "")) %>%
  kable_classic_2(html_font = "Times", fixed_thead = T, full_width = F) %>%
  add_header_above(c(" " = 2, "Time-only model" = 3, "Indepent var model" = 3, "Interaction model" = 3)) %>%
   footnote(
    general_title = "Note.",
    general = "*** = p < 0.001, ** = p < 0.01, * = p < 0.05",
    threeparttable = TRUE,
    footnote_as_chunk = TRUE
    ) %>%
    save_kable("/Users/anuschka/Documents/climatechange/climatechange/output/appendix/meta_regression_table_per_wave.png")

```


